---
title: |
  | **`r params$Year` Water Quality Annual Summary** 
  | `r params$Park`: `r params$Site`
output:
  pdf_document:
    latex_engine: xelatex
classoption: twocolumn
mainfont: Arial
header-includes:
- \pagenumbering{gobble}
geometry: margin=1cm
always_allow_html: true
params:
  Park: "NACE"
  Site: "OXRU"
  Year: "2024"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

```{r load packages, include=F}
##load packages
#library(tinytex)
#library(shiny)
#library(tidyr)
library(dplyr)
library(ggplot2)
#library(lubridate)
#library(knitr)
#library(cowplot)

```

```{r wq data, include=F}
metadata <- read.csv("wqp_ncrnwater_metadata.csv")
metadata <- metadata %>%
  tidyr::separate(SiteCode, c("Network", "Park", "Site"))

park <- metadata %>%
  dplyr::filter(Park==params$Park & Site==params$Site)

# park <- metadata %>%
#   dplyr::filter(Park=="NACE", Site=="OXRU")

mypark <- unique(park$LongName)
mysite <- unique(park$SiteName)

thresholds <- metadata %>%
  dplyr::select(SiteCodeWQX, DataName, LowerPoint, UpperPoint)

colnames(thresholds) <- c("MonitoringLocationIdentifier", "CharacteristicName", "LowerPoint", "UpperPoint")

##loading in data
wq_data <- read.csv("wqp.csv")

##selecting columns
wq_data1 <- wq_data %>%
  dplyr::select(ActivityStartDate, MonitoringLocationIdentifier,
         MonitoringLocationName, CharacteristicName, 
         ResultMeasureValue, ResultMeasure.MeasureUnitCode)

##converting date to date object
wq_data1$ActivityStartDate <- as.Date(wq_data1$ActivityStartDate, format = "%Y-%m-%d")
##extracting year
wq_data1$sample_year <- lubridate::year(wq_data1$ActivityStartDate)

##converting ResultMeasureValue to numeric object
wq_data1$ResultMeasureValue <- as.numeric(wq_data1$ResultMeasureValue)

wq_data1 <- wq_data1 %>%
  na.omit() 

wq_data_merged <- merge(wq_data1, thresholds,
                        by=c("MonitoringLocationIdentifier", 
                             "CharacteristicName"), all=T)

wq_data_merged <- wq_data_merged %>%
  tidyr::separate(MonitoringLocationIdentifier, c("Network", "Park", "Site")) %>%
  dplyr::filter(CharacteristicName %in% c("Acid Neutralizing Capacity (ANC)",
                                   "Total Nitrogen, mixed forms",
                                   "Total Phosphorus, mixed forms",
                                   "pH", "Dissolved oxygen (DO)",
                                   "Salinity", "Temperature, water"))

##data wrangling
wq_data2 <- wq_data_merged %>%
  dplyr::filter(CharacteristicName %in% c("Acid Neutralizing Capacity (ANC)",
                                   "Total Nitrogen, mixed forms",
                                   "Total Phosphorus, mixed forms",
                                   "pH", "Dissolved oxygen (DO)",
                                   "Salinity", "Temperature, water")) %>%
  dplyr::filter(sample_year>2018) %>%
  tidyr::separate(MonitoringLocationIdentifier, c("Network", "Park", "Site")) %>%
  dplyr::select(ActivityStartDate, Park, Site, MonitoringLocationName, CharacteristicName, ResultMeasureValue, ResultMeasure.MeasureUnitCode, sample_year, LowerPoint, UpperPoint) %>%
  dplyr::mutate(karst=case_when(Park=="ANTI" | Park=="HAFE" | Park=="MONO" ~ "karst",
                         Park!="ANTI" | Park!="HAFE" | Park!="MONO" ~ "non-karst")) %>%
  dplyr::mutate(nutrient_ecoregion=case_when(Park=="ANTI" | Park=="CATO" | Park=="HAFE" ~ "XI",
                                      Park!="ANTI" | Park!="CATO" | Park!="HAFE" ~ "IX")) %>%
  dplyr::mutate(cold_water=case_when(Park=="CATO" ~ "cold",
                              Park!="CATO" ~ "warm")) %>%
  dplyr::mutate(pass_fail=case_when(ResultMeasureValue>UpperPoint~"F",
                             ResultMeasureValue<LowerPoint~"F",
                             TRUE~"P")) %>%
  dplyr::mutate(ResultMeasure.MeasureUnitCode=case_when(ResultMeasure.MeasureUnitCode=="deg C"~"\u00B0C",
                                                 ResultMeasure.MeasureUnitCode!="deg C"~ResultMeasure.MeasureUnitCode)) %>%
  dplyr::mutate(UpperPoint=as.character(UpperPoint)) %>%
  dplyr::mutate(UpperPoint=case_when(CharacteristicName=="pH"~"9",
                              CharacteristicName!="pH"~UpperPoint)) %>%
  dplyr::select(ActivityStartDate, Park, Site, MonitoringLocationName, karst, nutrient_ecoregion, cold_water, CharacteristicName, ResultMeasureValue, ResultMeasure.MeasureUnitCode, sample_year, LowerPoint, UpperPoint, pass_fail) %>%
  dplyr::group_by(Site, CharacteristicName, sample_year) %>%
  ##calculating percent pass
  dplyr::mutate(percent_pass=(sum(pass_fail=="P")/sum(pass_fail=="P" | pass_fail=="F"))*100)
  # dplyr::mutate(text=case_when(percent_pass==100~"text1",
  #                              (percent_pass==100 & sample_year==2024) & (percent_pass!=100 & sample_year!=2024)~"text2",
  #                              percent_pass==0~"text3",
  #                              percent_pass!=0 & percent_pass!=100 & !(percent_pass==100 & sample_year==2024)~"text4")) %>%
  # dplyr::group_by(MonitoringLocationName, CharacteristicName) %>%
  # dplyr::mutate(last_ex=case_when(pass_fail=="F"~max(sample_year),
  #                                 pass_fail=="T"~NA))

##changing column names
colnames(wq_data2) <- c("Date", "Park", "Site", "SiteName","karst", 
                        "nutrient_ecoregion", "cold_water",
                        "CharacteristicName", "ResultMeasureValue", 
                        "unit", "sample_year", "LowerPoint","UpperPoint",
                        "pass_fail", "percent_pass")

# wq_data2$last_ex <- max(unique(wq_data2$sample_year[wq_data2$pass_fail=="F" & wq_data2$SiteName==mysite & wq_data2$CharacteristicName=="Total Phosphorus, mixed forms"]))

# wq_data2 <- wq_data2 %>%
#   dplyr::group_by(SiteName, CharacteristicName, sample_year) %>%
#   dplyr::mutate(obs_year=n()) %>%
#   dplyr::mutate(exceed=sum(pass_fail=="F"))

```

```{r park wq data, include=F}
##filtering data frame by parameters
park_data <- wq_data2 %>%
  dplyr::filter(Park==params$Park, Site==params$Site)

# park_data <- wq_data2 %>%
#   dplyr::filter(Park=="NACE", Site=="OXRU")

##2024 data
park_data_24 <- park_data %>%
  dplyr::filter(sample_year==2024) %>%
  dplyr::group_by(Site, CharacteristicName) %>%
  ##calculating percent pass
  dplyr::mutate(percent_pass=(sum(pass_fail=="P")/sum(pass_fail=="P" | pass_fail=="F"))*100) %>%
  ##adding minimum and maximum value columns
  dplyr::mutate(min=min(ResultMeasureValue),
         max=max(ResultMeasureValue)) %>%
  ##rounding to two decimal places in min and max columns
  dplyr::mutate(min=round(min, digits=2),
         max=round(max, digits=2)) %>%
  dplyr::group_by(Site, cold_water, karst, nutrient_ecoregion, CharacteristicName, unit, LowerPoint, UpperPoint, min, max, pass_fail, percent_pass) %>%
  dplyr::summarize() 
  # dplyr::mutate(exceed_description=case_when(percent_pass<50~"most",
  #                                            percent_pass>=50 & ))

##function to remove duplicate rows for parameters with both passing and failing values 
for(i in unique(park_data_24$CharacteristicName)) {
  if(nrow(park_data_24[park_data_24$CharacteristicName==i,])==2) {
    park_data_24 <- park_data_24[!(park_data_24$CharacteristicName==i &
                                     park_data_24$pass_fail=="P"),]
  } else{park_data_24 <- park_data_24}
}

##2019-23 data
park_data_19_23 <- park_data %>%
  dplyr::filter(sample_year!=2024) %>%
  dplyr::group_by(Site, CharacteristicName) %>%
  dplyr::mutate(percent_pass=(sum(pass_fail=="P")/sum(pass_fail=="P" | pass_fail=="F"))*100) %>%
  dplyr::group_by(Site, CharacteristicName, percent_pass) %>%
  dplyr::summarize()

```

<!--setting up data frame for table and figures-->
```{r table df, include=F}
##merging 2024 and 2019-23 data frames 
table <- merge(park_data_24, park_data_19_23, by="CharacteristicName")

##creating data frame for table
table <- table %>%
  dplyr::select(CharacteristicName, percent_pass.x, percent_pass.y) %>%
  ##rounding percent pass to two decimal places
  dplyr::mutate(percent_pass.x=round(percent_pass.x, digits=0)) %>%
  dplyr::mutate(percent_pass.y=round(percent_pass.y, digits=0)) 

table2 <- table %>%
  tidyr::pivot_longer(!(CharacteristicName), names_to="years", values_to="percent_pass") %>%
  dplyr::mutate(years=case_when(years=="percent_pass.x"~"2024",
                         years=="percent_pass.y"~"2019–23")) %>%
  dplyr::mutate(colors=case_when(percent_pass==100~"black",
                          percent_pass!=100~"#E32636")) %>%
  dplyr::mutate(x_pos=case_when(CharacteristicName=="Acid Neutralizing Capacity (ANC)"~1,
                         CharacteristicName=="Dissolved oxygen (DO)"~2,
                         CharacteristicName=="pH"~3,
                         CharacteristicName=="Salinity"~4,
                         CharacteristicName=="Total Nitrogen, mixed forms"~5,
                         CharacteristicName=="Total Phosphorus, mixed forms"~6,
                         CharacteristicName=="Temperature, water"~7)) %>%
  dplyr::select(CharacteristicName, x_pos, years, percent_pass, colors)

colnames(table2) = c("Parameter", "x_pos", "years", "percent_pass", "colors")

colors_list <- table2 %>%
  dplyr::group_by(Parameter, colors, years) %>%
  dplyr::summarize() 

colors_list <- colors_list[!colors_list$years=="2019–23",]

colors_list$Parameter=c("Acid neutralizing capacity", "Dissolved oxygen",
                        "Salinity", "Water temperature", "Total nitrogen",
                        "Total phosphorus", "PH")

colors_list <- colors_list[order(colors_list$Parameter),]

colors_list <- print(colors_list$colors)

```

<!--creating figure-->
```{r figure, echo=F, warning=F}
##creating bar graph
bar_graph <- ggplot() +
  geom_bar(data=table2, aes(x=as.factor(x_pos), y=percent_pass, fill=years),
           width=0.7, color="black", size=0.8, position="dodge", stat="identity") +
  scale_fill_manual(name="Years", values=c("gray85", "#8DA0CB")) +
  scale_x_discrete(labels=c("Acid\nneutralizing\ncapacity", "Dissolved\noxygen", "pH",
                             "Salinity", "Total\nnitrogen", "Total\nphosphorus", "Water\ntemperature")) +
  xlab("Parameter") +
  ylab("% Passing") +
  coord_cartesian(xlim=c(0.3, 7.6), ylim=c(0, 110), expand=F) +
  geom_text(data=table2, aes(x=as.factor(x_pos), y=percent_pass + 3.5, group=years, label=percent_pass, color=colors),
            position=position_dodge2(width=0.7, preserve="total"), size=3) +
  scale_color_manual(values=c("#E32636", "black"), guide="none") +
  theme_bw() +
  theme(axis.text.x=element_text(color=colors_list, size=9, angle=35, vjust=0.8, hjust=0.5),
        axis.title.x=element_text(vjust=3, size=12),
        axis.title.y=element_text(size=12),
        legend.position=c(0.8, -0.23),
        legend.direction="horizontal",
        plot.margin = unit(c(0.2,0.2,0.2,0.2), "cm"))

#bar_graph

```

<!--site photo-->
```{r site photo, echo=F}
fig_name <- paste(unique(park_data$Park), unique(park_data$Site), sep="_")

file_path <- paste("Site images/", fig_name, ".png", sep="")

#knitr::include_graphics(file_path)

site_image <- knitr::include_graphics(file_path)

```

<!--site map-->
```{r site map, echo=F}
 map_path <- paste("maps/", fig_name, "_map2.png", sep="")

# knitr::include_graphics(map_path)

site_map <- knitr::include_graphics(map_path)

```

```{r, echo=F}
##statements:
##if 100% pass always (percent_pass==100): [parameter] measurements at [site] have not exceeded the acceptable threshold since monitoring began in [year].
##if 100% pass in 2024, but not previously ((percent_pass==100 & year==2024) & (percent_pass!=100 & year!=2024)): The last [parameter] exceedance at [site] was recorded in [year].
##if parameter has never passed (percent_pass==0): [parameter] measurements at [site] have never met the acceptable threshold since monitoring began in [year].
##mean(percent_pass)!=0 & (percent_pass==0 & sample_year==2024): The last acceptable [parameter] measurement at [site] was recorded in [year].
##otherwise (percent_pass!=0 & percent_pass!=100 & !(percent_pass==100 & year==2024)): 

my_char <- ""

text <- function(df, site, char) {
  
  #assign("my_char", char, envir=.GlobalEnv)
  my_char <- paste(my_char, char)
  
  if (mean(df$percent_pass[df$SiteName==site & df$CharacteristicName==char])==100) {
    print(text1)
  } else if (unique(df$percent_pass[df$SiteName==site & df$CharacteristicName==char & df$sample_year==2024])==100 &
             mean(df$percent_pass[df$SiteName==site & df$CharacteristicName==char])!=100) {
    print(text2)
  } else if (mean(df$percent_pass[df$SiteName==site & df$CharacteristicName==char])==0) {
    print(text3)
  } else if (mean(df$percent_pass[df$SiteName==site & df$CharacteristicName==char])!=100 &
      mean(df$percent_pass[df$SiteName==site & df$CharacteristicName==char])!=0 &
      unique(df$percent_pass[df$sample_year==2024 & df$SiteName==site & df$CharacteristicName==char])!=100) {
    print(text5)
  }
    
}


##function to find last exceedance
find_last_ex <- function(df, site, char) {
  
  if(nrow(df[df$pass_fail=="F" & df$CharacteristicName==char,])!=0) {
    print(max(df$sample_year[df$pass_fail=="F" & df$SiteName==site & df$CharacteristicName==char]))
  } else {""}
      
}

##testing function 
find_last_ex(wq_data2, mysite, "Salinity")


##function to find last pass year
find_last_pass <- function(df, site, char) {
  
  if(nrow(df[df$pass_fail=="P" & df$CharacteristicName==char,])!=0) {
    print(max(df$sample_year[df$pass_fail=="P" & df$SiteName==site & df$CharacteristicName==char]))
  } else {""}
  
}

##testing function
find_last_pass(wq_data2, mysite, "Total Phosphorus, mixed forms")


##new data frame to find first year recorded
wq_first_year <- wq_data1 %>%
  dplyr::filter(CharacteristicName %in% c("Acid Neutralizing Capacity (ANC)",
                                   "Total Nitrogen, mixed forms",
                                   "Total Phosphorus, mixed forms",
                                   "pH", "Dissolved oxygen (DO)",
                                   "Salinity", "Temperature, water")) %>%
  tidyr::separate(MonitoringLocationIdentifier, c("Network", "Park", "Site"))

colnames(wq_first_year) <- c("ActivityStartDate", "Network", "Park", "Site", "SiteName", "CharacteristicName", "ResultMeasureValue", "unit", "sample_year")

##function to find first year recorded
find_first_year <- function(df, site, char) {
  
  print(min(df$sample_year[df$SiteName==site & df$CharacteristicName==char]))
  
}

##testing function
find_first_year(wq_first_year, mysite, "Total Phosphorus, mixed forms")


##text1
text1 <- paste(my_char, "measurements at", mysite, "have not exceeded the acceptable threshold since monitoring began in", sep=" ")
##[start year]

##text2
##The last [parameter]
text2 <- paste("The last", my_char, "exceedance at", mysite, "was recorded in", find_last_ex(wq_data2, mysite, my_char), sep=" ")

##text3
text3 <- paste(my_char, "measurements at", mysite, "have never met the acceptable threshold since monitoring began in", sep=" ")
##[start year]

##text4
text4 <- paste("The last acceptable", my_char, "measurement at", mysite, "was recorded in", find_last_pass(wq_data2, mysite, my_char), sep=" ")

##text5
text5 <- "test5"


##testing function
text(wq_data2, mysite, "Total Phosphorus, mixed forms")

```

```{r, echo=F}
##function to show increase or decrease in % pass
increase_decrease <- function(df, char) {
  
  if(df$percent_pass.x[df$CharacteristicName==char]>df$percent_pass.y[df$CharacteristicName==char]) {
    print("increased")
  } else if (df$percent_pass.x[df$CharacteristicName==char]<df$percent_pass.y[df$CharacteristicName==char]) {
    print("decreased")
  } else if (df$percent_pass.x[df$CharacteristicName==char]==df$percent_pass.y[df$CharacteristicName==char]) {
    print("remained the same")
  } 
  
}

##testing function
increase_decrease(table, "pH")

```


<!--function for adding icons to parameters with exceedances-->
```{r icons, include=F}
##creating function to print icons
icon <- function(df) {

  if (df$pass_fail=="F") {
    #"!"
    knitr::asis_output("\U2666")
    } else{" "} 

}

```

<!--print figure-->
```{r, echo=F, out.width="120%"}
bar_graph

```

Acid Neutralizing Capacity (ANC) \textbf{\textcolor{red}{`r icon(park_data_24[park_data_24$CharacteristicName=="Acid Neutralizing Capacity (ANC)",])`}}        
**Acceptable values:** Above `r park_data_24$LowerPoint[park_data_24$CharacteristicName=="Acid Neutralizing Capacity (ANC)"]` `r park_data_24$unit[park_data_24$CharacteristicName=="Acid Neutralizing Capacity (ANC)"]`   
**2024 range:** `r park_data_24$min[park_data_24$CharacteristicName=="Acid Neutralizing Capacity (ANC)"]` – `r park_data_24$max[park_data_24$CharacteristicName=="Acid Neutralizing Capacity (ANC)"]` `r park_data_24$unit[park_data_24$CharacteristicName=="Acid Neutralizing Capacity (ANC)"]`  
ANC is a measure of water’s ability to buffer acidic inputs. ANC measurements have never fallen below the acceptable threshold since monitoring began in 2005.  
   
Dissolved Oxygen (DO) \textbf{\textcolor{red}{`r icon(park_data_24[park_data_24$CharacteristicName=="Dissolved oxygen (DO)",])`}}    
**Acceptable values:** Above `r park_data_24$LowerPoint[park_data_24$CharacteristicName=="Dissolved oxygen (DO)"]` `r park_data_24$unit[park_data_24$CharacteristicName=="Dissolved oxygen (DO)"]`  
**2024 range:** `r park_data_24$min[park_data_24$CharacteristicName=="Dissolved oxygen (DO)"]` – `r park_data_24$max[park_data_24$CharacteristicName=="Dissolved oxygen (DO)"]` `r park_data_24$unit[park_data_24$CharacteristicName=="Dissolved oxygen (DO)"]`   
Aquatic organisms rely on DO to survive. Cooler water holds more DO, so measurements vary by season. DO has not fallen below the acceptable threshold since 2006.  
  
pH \textbf{\textcolor{red}{`r icon(park_data_24[park_data_24$CharacteristicName=="pH",])`}}    
**Acceptable range:** `r park_data_24$LowerPoint[park_data_24$CharacteristicName=="pH"]` – `r park_data_24$UpperPoint[park_data_24$CharacteristicName=="pH"]`    
**2024 range:** `r park_data_24$min[park_data_24$CharacteristicName=="pH"]` – `r park_data_24$max[park_data_24$CharacteristicName=="pH"]`  
pH is a measure of how acidic or basic a liquid is.  pH measurements have fallen within the acceptable range since monitoring began in 2005.  
  
Salinity \textbf{\textcolor{red}{`r icon(park_data_24[park_data_24$CharacteristicName=="Salinity",])`}}    
**Acceptable values:** Below `r park_data_24$UpperPoint[park_data_24$CharacteristicName=="Salinity"]` `r park_data_24$unit[park_data_24$CharacteristicName=="Salinity"]`  
**2024 range:** `r park_data_24$min[park_data_24$CharacteristicName=="Salinity"]` – `r park_data_24$max[park_data_24$CharacteristicName=="Salinity"]` `r park_data_24$unit[park_data_24$CharacteristicName=="Salinity"]`  
Road salt is the main cause of high salinity in NCR streams.  Salinity has not surpassed the acceptable threshold at Flowing Springs Run since 2017.  
  
Total Nitrogen \textbf{\textcolor{red}{`r icon(park_data_24[park_data_24$CharacteristicName=="Total Nitrogen, mixed forms",])`}}   
**Acceptable values:** Below `r park_data_24$UpperPoint[park_data_24$CharacteristicName=="Total Nitrogen, mixed forms"]` `r park_data_24$unit[park_data_24$CharacteristicName=="Total Nitrogen, mixed forms"]`  
**2024 range:** `r park_data_24$min[park_data_24$CharacteristicName=="Total Nitrogen, mixed forms"]` – `r park_data_24$max[park_data_24$CharacteristicName=="Total Nitrogen, mixed forms"]` `r park_data_24$unit[park_data_24$CharacteristicName=="Total Nitrogen, mixed forms"]`  
Nitrogen is commonly used in agricultural fertilizers. Under high concentrations, it can adversely affect aquatic life. All total nitrogen measurements since 2016 have exceeded the acceptable threshold.  

<!--print images-->
```{r, echo=F, fig.show='hold', out.width="70%", fig.ncol=2, fig.align="right"}
 
site_image
site_map

```
  
Total Phosphorus \textbf{\textcolor{red}{`r icon(park_data_24[park_data_24$CharacteristicName=="Total Phosphorus, mixed forms",])`}}   
**Acceptable values:** Below `r park_data_24$UpperPoint[park_data_24$CharacteristicName=="Total Phosphorus, mixed forms"]` `r park_data_24$unit[park_data_24$CharacteristicName=="Total Phosphorus, mixed forms"]`  
**2024 range:** `r park_data_24$min[park_data_24$CharacteristicName=="Total Phosphorus, mixed forms"]` – `r park_data_24$max[park_data_24$CharacteristicName=="Total Phosphorus, mixed forms"]` `r park_data_24$unit[park_data_24$CharacteristicName=="Total Phosphorus, mixed forms"]`  
Phosphorus is often a limiting nutrient in freshwater streams, meaning a small increase in phosphorus concentration can lead to algal blooms. All observations in 2024 exceeded the threshold.  
  
Water Temperature \textbf{\textcolor{red}{`r icon(park_data_24[park_data_24$CharacteristicName=="Temperature, water",])`}}    
**Acceptable values:** Below `r park_data_24$UpperPoint[park_data_24$CharacteristicName=="Temperature, water"]` `r park_data_24$unit[park_data_24$CharacteristicName=="Temperature, water"]`  
**2024 range:** `r park_data_24$min[park_data_24$CharacteristicName=="Temperature, water"]` – `r park_data_24$max[park_data_24$CharacteristicName=="Temperature, water"]` `r park_data_24$unit[park_data_24$CharacteristicName=="Temperature, water"]`   
Water temperature measurements have remained below the acceptable threshold since monitoring began in 2005.  
  
**Water Quality Monitoring in the NCR**  
Data on additional water quality parameters, including depth, discharge, conductivity, and total dissolved solids, are available in the [NCRN water quality data visualizer](https://irma.nps.gov/DataStore/Reference/Profile/2237386). Visit the [NCRN water quality monitoring webpage](https://www.nps.gov/im/ncrn/water.htm) to learn more.
