---
output:
  pdf_document:
    latex_engine: xelatex
fontsize: 11pt
urlcolor: RoyalBlue
classoption: twocolumn
mainfont: Arial
header-includes:
- \pagenumbering{gobble}
- \setlength{\columnsep}{2em}
- \setlength{\headheight}{13.6pt}
- \addtolength{\topmargin}{-15pt}
- \usepackage{fancyhdr}
- \usepackage{hyperref}
- \pagestyle{fancy}
- \fancyfoot[L]{\normalsize \color{red}`r knitr::asis_output("\U25B2")` \color{black}Red triangles indicate parameters that exceeded the acceptable threshold at least once in 2024.\\An \textbf{accessible HTML version} of this document is available in the \textbf{\href{https://irma.nps.gov/DataStore/Reference/Profile/2316392}{{NPS DataStore}}}.}
- \fancypagestyle{plain}{\pagestyle{fancy}}
- \renewcommand{\headrulewidth}{0pt}
geometry: margin=1.5cm
always_allow_html: true
params:
  Park: "MONO"
  Site: "BUCK"
  Year: "2024"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

```{r load packages, include=F}
##load packages
library(dplyr)
library(ggplot2)

```

```{r meta data, include=F}
metadata <- read.csv("wqp_ncrnwater_metadata.csv") %>%
  tidyr::separate(SiteCode, c("Network", "Park", "Site")) %>%
  ##changing Rock Creek at Dumbarton Oaks to Downstream of Dumbarton Oaks
  dplyr::mutate(SiteName=case_when(SiteName=="Rock Creek at Dumbarton Oaks"~"Rock Creek Downstream of Dumbarton Oaks",
                               TRUE~SiteName)) %>%
  ##creating column specifying karst v non-karst, cold vs warmwater, and nutrient ecoregion
  dplyr::mutate(karst=case_when(Park=="ANTI" | Park=="HAFE" | Park=="MONO" ~ "karst",
                         Park!="ANTI" | Park!="HAFE" | Park!="MONO" ~ "non-karst")) %>%
  dplyr::mutate(nutrient_ecoregion=case_when(Park=="ANTI" | Park=="CATO" | Park=="HAFE" ~ "XI",
                                      Park!="ANTI" | Park!="CATO" | Park!="HAFE" ~ "IX")) %>%
  dplyr::mutate(cold_water=case_when(Park=="CATO" ~ "coldwater",
                              Park!="CATO" ~ "warmwater")) 
  
##filtering for park/site
park <- metadata %>%
  dplyr::filter(Park==params$Park & Site==params$Site)

##setting park, site, and year variables
mypark <- unique(park$LongName)
mysite <- unique(park$SiteName)

myyear <- params$Year

start_year <- (as.numeric(myyear))-5
end_year <- (as.numeric(myyear))-1
five_yr_range <- paste(as.character(start_year), as.character(end_year), sep="\U2013")

```


---
title: |
  | \vspace{-2em} \huge \textbf{`r params$Year` Water Quality Summary} 
  | \LARGE `r mypark`: `r mysite` \vspace{-1em}
---


```{r wq data, include=F}
##creating data frame with exceedance thresholds
thresholds <- park %>%
  dplyr::select(DataName, LowerPoint, UpperPoint, Units, karst, 
                nutrient_ecoregion, cold_water) 

colnames(thresholds) <- c("CharacteristicName", "LowerPoint", "UpperPoint", "Units",
                          "karst", "nutrient_ecoregion", "cold_water")

##loading in water quality data
wq_data <- read.csv("wqp.csv")
# wq_data <- read.csv("wqp.csv") %>%
#   dplyr::mutate(MonitoringLocationName=case_when(MonitoringLocationName=="Battery Kemble Run"~"Battery Kemble Creek",
#                                                  TRUE~MonitoringLocationName))

##selecting columns
wq_data1 <- wq_data %>%
  dplyr::select(ActivityStartDate,
         MonitoringLocationName, CharacteristicName, 
         ResultMeasureValue) %>%
  dplyr::filter(MonitoringLocationName==mysite)

##converting date to date object
wq_data1$ActivityStartDate <- as.Date(wq_data1$ActivityStartDate, format = "%Y-%m-%d")

##extracting year
wq_data1$sample_year <- lubridate::year(wq_data1$ActivityStartDate)
wq_data1$sample_month <- lubridate::month(wq_data1$ActivityStartDate, label=T, abbr=F)
wq_data1$sample_my <- format(wq_data1$ActivityStartDate, "%B %Y")

##converting ResultMeasureValue to numeric object
wq_data1$ResultMeasureValue <- as.numeric(wq_data1$ResultMeasureValue) 

##removing NAs
wq_data1 <- wq_data1 %>%
  na.omit()

##merging wq and threshold data frames
wq_data_total <- merge(wq_data1, thresholds,
                        by=c("CharacteristicName"), all=T) %>%
  ##filtering for parameters of interest
  dplyr::filter(CharacteristicName %in% c("Acid Neutralizing Capacity (ANC)",
                                   "Total Nitrogen, mixed forms",
                                   "Total Phosphorus, mixed forms",
                                   "pH", "Dissolved oxygen (DO)",
                                   "Specific conductance", "Temperature, water")) %>%
  ##creating column with shortened parameter names for report
  dplyr::mutate(CharNameShort=case_when(CharacteristicName=="Acid Neutralizing Capacity (ANC)"~"ANC",
                                             CharacteristicName=="Dissolved oxygen (DO)"~"DO",
                                             CharacteristicName=="pH"~"pH",
                                             CharacteristicName=="Specific conductance"~"Specific conductance",
                                             CharacteristicName=="Temperature, water"~"Water temperature",
                                             CharacteristicName=="Total Nitrogen, mixed forms"~"Total nitrogen",
                                             CharacteristicName=="Total Phosphorus, mixed forms"~"Total phosphorus")) %>%
  ##creating column with lower case parameter names for report
  dplyr::mutate(CharNameLower=case_when(CharNameShort=="Specific conductance"~"specific conductance",
                                     CharNameShort=="Water temperature"~"water temperature",
                                     CharNameShort=="Total nitrogen"~"total nitrogen",
                                     CharNameShort=="Total phosphorus"~"total phosphorus",
                                     TRUE~CharNameShort)) %>%
  ##creating pass/fail column
  dplyr::mutate(pass_fail=case_when(ResultMeasureValue>=UpperPoint~"F",
                             ResultMeasureValue<=LowerPoint~"F",
                             TRUE~"P")) %>%
  ##calculating percent pass for each parameter per sampling year
  dplyr::group_by(CharacteristicName, sample_year) %>%
  dplyr::mutate(percent_pass=(sum(pass_fail=="P")/sum(pass_fail=="P" | pass_fail=="F"))*100) %>%
  dplyr::mutate(percent_pass=round(percent_pass, digits=0)) %>%
  ##creating pH exceedance column
  dplyr::mutate(pH_exceed=case_when(pass_fail=="F" & CharacteristicName=="pH" & ResultMeasureValue>9~"basic",
                                    pass_fail=="F" & CharacteristicName=="pH" & ResultMeasureValue<6~"acidic")) %>%
  ##finding maximum and minimum values for each parameter and sampling year
  dplyr::group_by(sample_year, CharacteristicName) %>%
  dplyr::mutate(min=min(ResultMeasureValue),
         max=max(ResultMeasureValue)) %>%
  ##rounding to two decimal places in min and max columns
  dplyr::mutate(min=case_when(CharNameShort=="Total phosphorus"~round(min, digits=3),
                              TRUE~round(min, digits=2)),
         max=case_when(CharNameShort=="Total phosphorus"~round(max, digits=3),
                              TRUE~round(max, digits=2)))

##changing column names
colnames(wq_data_total) <- c("CharacteristicName", "Date", "SiteName",
                             "ResultMeasureValue", "sample_year", "sample_month",
                             "month_year", "LowerPoint","UpperPoint", "unit",
                             "karst", "nutrient_ecoregion", "cold_water",
                             "CharNameShort", "CharNameLower", "pass_fail",
                             "percent_pass", "pH_exceed", "min", "max")

##creating data frame for current year + last 5 years
wq_data2 <- wq_data_total %>%
  dplyr::filter(sample_year>=start_year)

```


```{r park wq data, include=F}
## creating data frame for current data
park_data_current <- wq_data2 %>%
  dplyr::filter(sample_year==myyear) %>%
  ##filtering out unneeded columns 
  dplyr::select(-Date, -ResultMeasureValue, -sample_month, -month_year, 
                -pass_fail, -pH_exceed) %>%
  distinct() %>%
  ##creating column of text for parameters with percent pass between 1 and 99
  dplyr::mutate(major_P_F=case_when(percent_pass>50~paste("The majority of", CharNameLower, "measurements were acceptable at", mysite, "in", myyear, sep=" "),
                                    percent_pass<50 & percent_pass>0~paste("The majority of", CharNameLower, "measurements were not acceptable at", mysite, "in", myyear, sep=" "),
                                    percent_pass==50~paste("Half of", CharNameLower, "measurements were acceptable at", mysite, "in", myyear, sep=" ")))

##adding back pass_fail column 
park_data_current$pass_fail <- ifelse(park_data_current$percent_pass==100, "P", "F") 


##creating data frame for data from last 5 years
park_data_past <- wq_data2 %>%
  dplyr::filter(sample_year!=myyear) %>%
  dplyr::group_by(CharacteristicName) %>%
  dplyr::summarize(percent_pass=(sum(pass_fail=="P")/sum(pass_fail=="P" | pass_fail=="F"))*100) %>%
  dplyr::mutate(percent_pass=round(percent_pass, digits=0))

```

<!--setting up data frame for table and figures-->
```{r merged df, include=F}
##merging current and past data frames 
park_merged_wide <- merge(park_data_current, park_data_past, by="CharacteristicName") %>%
  dplyr::select(CharacteristicName, CharNameShort, CharNameLower,
                percent_pass.x, major_P_F, percent_pass.y) 

##pivoting dataframe so that current and past data are different categories in the same column 
park_merged_long <- park_merged_wide %>%
  tidyr::pivot_longer(!(CharacteristicName | CharNameShort | CharNameLower | major_P_F), names_to="years", values_to="percent_pass") %>%
  ##changing year names
  dplyr::mutate(years=case_when(years=="percent_pass.x"~as.character(myyear),
                         years=="percent_pass.y"~five_yr_range)) %>%
  dplyr::mutate(colors=case_when(percent_pass==100~"black",
                          percent_pass!=100~"#E32636")) %>%
  ##assigning numbers to parameters for easy graphing
  dplyr::mutate(x_pos=case_when(CharacteristicName=="Acid Neutralizing Capacity (ANC)"~1,
                         CharacteristicName=="Dissolved oxygen (DO)"~2,
                         CharacteristicName=="pH"~3,
                         CharacteristicName=="Specific conductance"~4,
                         CharacteristicName=="Total Nitrogen, mixed forms"~5,
                         CharacteristicName=="Total Phosphorus, mixed forms"~6,
                         CharacteristicName=="Temperature, water"~7)) 

colnames(park_merged_long) = c("Parameter", "CharNameShort", "CharNameLower", "major_P_F", "years", "percent_pass", "colors", "x_pos")

```

<!--creating figure-->
```{r create figure, echo=F, warning=F}
##creating bar graph
bar_graph <- ggplot() +
  geom_bar(data=park_merged_long, aes(x=as.factor(x_pos), y=percent_pass, fill=years),
           width=0.7, color="black", size=0.8, position="dodge", stat="identity") +
  scale_fill_manual(name="Years", values=c("gray85", "#8DA0CB")) +
  scale_x_discrete(labels=c("Acid\nneutralizing\ncapacity", "Dissolved\noxygen", "pH",
                             "Specific\nconductance", "Total\nnitrogen", "Total\nphosphorus", "Water\ntemperature")) +
  coord_cartesian(xlim=c(0.3, 7.6), ylim=c(0, 110), expand=F) +
  geom_text(data=park_merged_long, aes(x=as.factor(x_pos), y=percent_pass + 3.5, group=years, label=percent_pass, color=colors),
            position=position_dodge2(width=0.7, preserve="total"), size=4) +
  scale_color_manual(values=c("#E32636", "black"), guide="none") +
  theme_bw() +
  theme(axis.text.x=element_text(color="black", size=11, angle=35, vjust=0.6, hjust=0.5),
        axis.text.y=element_text(size=11),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        legend.text=element_text(size=11),
        legend.title=element_blank(),
        legend.position=c(0.095, -0.30),
        legend.direction="horizontal",
        plot.margin = unit(c(0,0.2,0.8,0), "cm"))

#bar_graph

```

<!--site photo-->
```{r setting up site photo, echo=F}
##setting image name
fig_name <- paste(unique(park$Park), unique(park$Site), sep="_")

##setting image file path
file_path <- paste("Site images/", fig_name, ".png", sep="")

##creating object to print image
site_image <- knitr::include_graphics(file_path)

```

<!--automating text-->
<!--last exceedance/last pass/first record functions (no longer used)-->
```{r functions, echo=F, include=F, warning=F}
##function to find month and year of last exceedance
find_last_ex <- function(df, char) {
  
  print(unique(na.omit(df$month_year[df$Date==max(df$Date[df$pass_fail=="F" & df$CharNameShort==char])])))
      
}

##testing function 
find_last_ex(wq_data_total, "Total phosphorus")


##function to find month and year last passing measurement
find_last_pass <- function(df, char) {
  
  print(unique(na.omit(df$month_year[df$Date==max(df$Date[df$pass_fail=="P" & df$CharNameShort==char], na.rm=T)])))
  
}

##testing function
find_last_pass(wq_data_total, "Total phosphorus")


##function to find first year a parameter was recorded
find_first_year <- function(df, char) {
  
  print(min(df$sample_year[df$CharNameShort==char], na.rm=T))
  
}

##testing function
find_first_year(wq_data_total, "Total nitrogen")

```

<!--increasing/decreasing % passing function-->
```{r increase decrease, echo=F, include=F, warning=F}
##function to show increase/decrease in % pass and magnitude of change between past and current data 
increase_decrease <- function(df, char) {
  
  if(df$percent_pass.x[df$CharNameShort==char]-df$percent_pass.y[df$CharNameShort==char] >= 25) {
    print("increased considerably")
  } else if (df$percent_pass.x[df$CharNameShort==char]-df$percent_pass.y[df$CharNameShort==char] < 25 & df$percent_pass.x[df$CharNameShort==char]-df$percent_pass.y[df$CharNameShort==char] >= 10) {
    print("increased")
  } else if (df$percent_pass.x[df$CharNameShort==char]-df$percent_pass.y[df$CharNameShort==char] < 10 & df$percent_pass.x[df$CharNameShort==char]-df$percent_pass.y[df$CharNameShort==char] > 0) {
    print("increased slightly")
  } else if (df$percent_pass.x[df$CharNameShort==char]-df$percent_pass.y[df$CharNameShort==char] < 0 & df$percent_pass.x[df$CharNameShort==char]-df$percent_pass.y[df$CharNameShort==char] > -10) {
    print("decreased slightly")
  } else if (df$percent_pass.x[df$CharNameShort==char]-df$percent_pass.y[df$CharNameShort==char] <= -10 & df$percent_pass.x[df$CharNameShort==char]-df$percent_pass.y[df$CharNameShort==char] > -25) {
    print("decreased")
  } else if (df$percent_pass.x[df$CharNameShort==char]-df$percent_pass.y[df$CharNameShort==char] < -25) {
    print("decreased considerably")
  } else if (df$percent_pass.x[df$CharNameShort==char]==df$percent_pass.y[df$CharNameShort==char]) {
    print("remained the same")
  } 
  
}

##testing function
increase_decrease(park_merged_wide, "ANC")

```

<!--pH exceedance function-->
```{r pH exceed, echo=F, include=F, warning=F}
##creating dataframe with only pH
pH_df <- wq_data_total[wq_data_total$CharacteristicName=="pH" & wq_data_total$sample_year>2018,]

##function to show directionality of pH exceedances
ph_ex <- function(df) {
  
  if(nrow(df[df$pH_exceed=="acidic",]) > nrow(df[df$pH_exceed=="basic",])) {
    paste("Most pH exceedances at", mysite, "are acidic (lower than 6).", sep=" ")
  } else if(nrow(df[df$pH_exceed=="basic",]) > nrow(df[df$pH_exceed=="acidic",])) {
    paste("Most pH exceedances at", mysite, "are basic (greater than 9).", sep=" ") 
  } else {
      print("")
    }
  
}

##testing function
ph_ex(pH_df)

```

<!--text printing function-->
```{r text automation, echo=F, include=F, warning=F}
##statements:
##if 100% pass in current year and 5 years prior: text1
##if 0% pass in current year and 5 years prior: text3
##if 100% pass in current year but not before: text 2 + text 7
##if 0% pass in current year but not before: text 4 + text 7
##if neither 0 nor 100% pass in current year and changed from 5 years prior: text5
##if neither 0 nor 100% pass in current year and same value as 5 years prior: text 6

##creating function to paste text
write_text <- function(df, char, data_wide, data_long) {
  
  ##text options
  text1 <- paste("All", data_wide$CharNameLower[data_wide$CharNameShort==char], "measurements at", mysite, "were passing in", myyear, "and the five years prior.", sep=" ")
  text2 <- paste("All", data_wide$CharNameLower[data_wide$CharNameShort==char], "measurements at", mysite, "were passing in", myyear, sep=" ")
  text3 <- paste("All", data_wide$CharNameLower[data_wide$CharNameShort==char], "measurements at", mysite, "exceeded the acceptable threshold", "in", myyear, "and the five years prior.", sep=" ")
  text4 <- paste("All", data_wide$CharNameLower[data_wide$CharNameShort==char], "measurements at", mysite, "exceeded the acceptable threshold", "in", myyear, sep=" ")
  text5 <- paste(paste(data_long$major_P_F[data_long$CharNameShort==char & data_long$years==myyear], ".", sep=""),"The percentage of passing measurements",  
                 increase_decrease(data_wide, char), "compared to the five years prior.", sep=" ")
  text6 <- paste(paste(data_long$major_P_F[data_long$CharNameShort==char & data_long$years==myyear], ".", sep=""),"The percentage of passing measurements",  
                 increase_decrease(data_wide, char), "as the five years prior.", sep=" " )
  text7 <- paste("The percentage of passing measurements",  increase_decrease(data_wide, char), "compared to the five years prior.", sep=" ")
  
  ##conditions for each text option
  if (mean(df$percent_pass[df$CharNameShort==char & df$sample_year>=start_year], na.rm=T)==100) {
    my_text <- text1
  } else if (mean(df$percent_pass[df$CharNameShort==char & df$sample_year==myyear], na.rm=T)==100 &
             mean(df$percent_pass[df$CharNameShort==char & df$sample_year>=start_year], na.rm=T)!=100) {
    my_text <- paste(paste(text2, ".", sep=""), text7, sep=" ")
  } else if (mean(df$percent_pass[df$CharNameShort==char & df$sample_year>=start_year], na.rm=T)==0) {
    my_text <- text3
  } else if (mean(df$percent_pass[df$CharNameShort==char & df$sample_year==myyear], na.rm=T)==0 &
             mean(df$percent_pass[df$CharNameShort==char & df$sample_year>=start_year], na.rm=T)!=0) {
    my_text <- paste(paste(text4, ".", sep=""), text7, sep=" ")
  } else if (increase_decrease(data_wide, char) %in% c("decreased considerably", "decreased", "decreased slightly", "increased considerably", "increased", "increased slightly")) {
    my_text<-text5
  } else if (mean(df$percent_pass[df$CharNameShort==char & df$sample_year>=start_year], na.rm=T)!=100 &
             mean(df$percent_pass[df$CharNameShort==char & df$sample_year>=start_year], na.rm=T)!=0 &
             increase_decrease(data, char)=="remained the same") {
    my_text <- text6
  }else {
    my_text <- print("test")
  }
  
  return(my_text)
    
}

##testing function
write_text(wq_data_total, "Total phosphorus", park_merged_wide, park_merged_long)

```

<!--function for adding icons to parameters with exceedances-->
```{r icons, include=F}
##creating function to print icons
icon <- function(df) {

  if (df$pass_fail=="F") {
    knitr::asis_output("\U25B2")
    } else{" "} 

}

##testing function
icon(park_data_current[park_data_current$CharacteristicName=="Acid Neutralizing Capacity (ANC)",])

```

\Large \textbf{Percent of Measurements Passing}
\vspace{-1.5em}
<!--print figure-->
```{r print figure, echo=F, out.width="120%", fig.align="left"}
bar_graph

```
  
  
\Large \textbf{Acid Neutralizing Capacity (ANC)} \textbf{\textcolor{red}{`r icon(park_data_current[park_data_current$CharacteristicName=="Acid Neutralizing Capacity (ANC)",])`}}       
\normalsize \textbf{Acceptable values:} Above `r park_data_current$LowerPoint[park_data_current$CharacteristicName=="Acid Neutralizing Capacity (ANC)"]` `r park_data_current$unit[park_data_current$CharacteristicName=="Acid Neutralizing Capacity (ANC)"]`   
\textbf{`r myyear` range:} `r park_data_current$min[park_data_current$CharacteristicName=="Acid Neutralizing Capacity (ANC)"]` – `r park_data_current$max[park_data_current$CharacteristicName=="Acid Neutralizing Capacity (ANC)"]` `r park_data_current$unit[park_data_current$CharacteristicName=="Acid Neutralizing Capacity (ANC)"]`  
`r write_text(wq_data_total, "ANC", park_merged_wide, park_merged_long)`  
\vspace{1pt}   
\Large \textbf{Dissolved Oxygen (DO)} \textbf{\textcolor{red}{`r icon(park_data_current[park_data_current$CharacteristicName=="Dissolved oxygen (DO)",])`}}    
\normalsize \textbf{Acceptable values:} Above `r park_data_current$LowerPoint[park_data_current$CharacteristicName=="Dissolved oxygen (DO)"]` `r park_data_current$unit[park_data_current$CharacteristicName=="Dissolved oxygen (DO)"]`  
\textbf{`r myyear` range:} `r park_data_current$min[park_data_current$CharacteristicName=="Dissolved oxygen (DO)"]` – `r park_data_current$max[park_data_current$CharacteristicName=="Dissolved oxygen (DO)"]` `r park_data_current$unit[park_data_current$CharacteristicName=="Dissolved oxygen (DO)"]`   
`r write_text(wq_data_total, "DO", park_merged_wide, park_merged_long)`  
\vspace{1pt}   
\Large \textbf{pH} \textbf{\textcolor{red}{`r icon(park_data_current[park_data_current$CharacteristicName=="pH",])`}}    
\normalsize \textbf{Acceptable range:} `r park_data_current$LowerPoint[park_data_current$CharacteristicName=="pH"]` – `r park_data_current$UpperPoint[park_data_current$CharacteristicName=="pH"]`    
\textbf{`r myyear` range:} `r park_data_current$min[park_data_current$CharacteristicName=="pH"]` – `r park_data_current$max[park_data_current$CharacteristicName=="pH"]`  
`r write_text(wq_data_total, "pH", park_merged_wide, park_merged_long)` `r ph_ex(pH_df)`  
\vspace{1pt}   
\Large \textbf{Specific Conductance} \textbf{\textcolor{red}{`r icon(park_data_current[park_data_current$CharacteristicName=="Specific conductance",])`}}    
\normalsize \textbf{Acceptable values:} Below `r park_data_current$UpperPoint[park_data_current$CharacteristicName=="Specific conductance"]` `r park_data_current$unit[park_data_current$CharacteristicName=="Specific conductance"]`  
\textbf{`r myyear` range:} `r park_data_current$min[park_data_current$CharacteristicName=="Specific conductance"]` – `r park_data_current$max[park_data_current$CharacteristicName=="Specific conductance"]` `r park_data_current$unit[park_data_current$CharacteristicName=="Specific conductance"]`  
`r write_text(wq_data_total, "Specific conductance", park_merged_wide, park_merged_long)`  


<!--column break-->
\vfill\eject
  
$$\\[-1.55em]$$

<!--print site image-->
```{r, echo=F, out.width="85%", fig.align="right", fig.alt = "test"}
#site_map
site_image

```

\vspace{-1.5em}
\begin{flushright}
\begin{minipage}{0.85\columnwidth}
\small `r mysite` is a `r unique(park_data_current$cold_water)` `r unique(park_data_current$karst)` stream.
\end{minipage}
\end{flushright}

$$\\[-2.85em]$$
<!-- \vspace{4.5pt}   -->

\Large \textbf{Total Nitrogen} \textbf{\textcolor{red}{`r icon(park_data_current[park_data_current$CharacteristicName=="Total Nitrogen, mixed forms",])`}}   
\normalsize \textbf{Acceptable values:} Below `r park_data_current$UpperPoint[park_data_current$CharacteristicName=="Total Nitrogen, mixed forms"]` `r park_data_current$unit[park_data_current$CharacteristicName=="Total Nitrogen, mixed forms"]`  
\textbf{`r myyear` range:} `r park_data_current$min[park_data_current$CharacteristicName=="Total Nitrogen, mixed forms"]` – `r park_data_current$max[park_data_current$CharacteristicName=="Total Nitrogen, mixed forms"]` `r park_data_current$unit[park_data_current$CharacteristicName=="Total Nitrogen, mixed forms"]`  
`r write_text(wq_data_total, "Total nitrogen", park_merged_wide, park_merged_long)`  
\vspace{-1pt}  
\Large \textbf{Total Phosphorus} \textbf{\textcolor{red}{`r icon(park_data_current[park_data_current$CharacteristicName=="Total Phosphorus, mixed forms",])`}}   
\normalsize \textbf{Acceptable values:} Below `r park_data_current$UpperPoint[park_data_current$CharacteristicName=="Total Phosphorus, mixed forms"]` `r park_data_current$unit[park_data_current$CharacteristicName=="Total Phosphorus, mixed forms"]`  
\textbf{`r myyear` range:} `r park_data_current$min[park_data_current$CharacteristicName=="Total Phosphorus, mixed forms"]` – `r park_data_current$max[park_data_current$CharacteristicName=="Total Phosphorus, mixed forms"]` `r park_data_current$unit[park_data_current$CharacteristicName=="Total Phosphorus, mixed forms"]`  
`r write_text(wq_data_total, "Total phosphorus", park_merged_wide, park_merged_long)`  
\vspace{-1pt}  
\Large \textbf{Water Temperature} \textbf{\textcolor{red}{`r icon(park_data_current[park_data_current$CharacteristicName=="Temperature, water",])`}}    
\normalsize \textbf{Acceptable values:} Below `r park_data_current$UpperPoint[park_data_current$CharacteristicName=="Temperature, water"]` `r park_data_current$unit[park_data_current$CharacteristicName=="Temperature, water"]`  
\textbf{`r myyear` range:} `r park_data_current$min[park_data_current$CharacteristicName=="Temperature, water"]` – `r park_data_current$max[park_data_current$CharacteristicName=="Temperature, water"]` `r park_data_current$unit[park_data_current$CharacteristicName=="Temperature, water"]`   
`r write_text(wq_data_total, "Water temperature", park_merged_wide, park_merged_long)`    
\vspace{2pt}   
\Large \textbf{Water Quality Monitoring in the NCR}  
\normalsize This report summarizes water quality data from `r start_year` to `r myyear` for seven parameters. The National Capital Region Inventory & Monitoring Network (NCRN I&M) monitors additional water quality parameters, including depth, discharge, conductivity, and total dissolved solids. These data are available in the [NCRN I\&M water quality data visualizer](https://irma.nps.gov/DataStore/Reference/Profile/2237386). Visit the [NCRN I&M water quality monitoring webpage](https://www.nps.gov/im/ncrn/water.htm) to learn more.  
  

