---
title: |
  | `r params$Year` Water Quality Annual Summary: 
  | `r params$Park`, `r params$Site`
output: pdf_document
classoption:
  - twocolumn
params:
  Park: "Prince William Forest Park"
  Site: "Orenda Run"
  Year: "2024"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load packages, include=F}
##load packages
library(tinytex)
library(shiny)
library(tidyr)
library(dplyr)
library(ggplot2)
library(lubridate)
library(knitr)
#install.packages("kableExtra")
library(kableExtra)
#install.packages("Rmoji")
library(Rmoji)
#install.packages("plotly")
library(plotly)
library(ggplot2)

```


```{r wq data, include=F}
##loading in data
current_wd <- getwd()
setwd(current_wd)
wq_data <- read.csv("wqp.csv")

##selecting columns
wq_data1 <- wq_data[, c("ActivityStartDate", "MonitoringLocationIdentifier",
                       "MonitoringLocationName", "CharacteristicName", 
                       "ResultMeasureValue", "ResultMeasure.MeasureUnitCode")]

##converting date to date object
wq_data1$ActivityStartDate <- as.Date(wq_data1$ActivityStartDate, format = "%Y-%m-%d")
##extracting year
wq_data1$year <- year(wq_data1$ActivityStartDate)

##converting ResultMeasureValue to numeric object
wq_data1$ResultMeasureValue <- as.numeric(wq_data1$ResultMeasureValue)

##data wrangling
wq_data2 <- wq_data1 %>%
  na.omit() %>%
  filter(CharacteristicName %in% c("Acid Neutralizing Capacity (ANC)",
                                   "Total Nitrogen, mixed forms",
                                   "Total Phosphorus, mixed forms",
                                   "pH", "Dissolved oxygen (DO)",
                                   "Salinity", "Temperature, water")) %>%
  filter(year>2018) %>%
  separate(MonitoringLocationIdentifier, c("Network", "Park", "Site")) %>%
  select(ActivityStartDate, Park, Site, MonitoringLocationName, CharacteristicName, ResultMeasureValue, ResultMeasure.MeasureUnitCode, year) %>%
  mutate(karst=case_when(Park=="ANTI" | Park=="HAFE" | Park=="MONO" ~ "karst",
                         Park!="ANTI" | Park!="HAFE" | Park!="MONO" ~ "non-karst")) %>%
  mutate(nutrient_ecoregion=case_when(Park=="ANTI" | Park=="CATO" | Park=="HAFE" ~ "XI",
                                      Park!="ANTI" | Park!="CATO" | Park!="HAFE" ~ "IX")) %>%
  mutate(cold_water=case_when(Park=="CATO" ~ "cold",
                              Park!="CATO" ~ "warm")) %>%
  mutate(threshold=case_when(CharacteristicName=="Acid Neutralizing Capacity (ANC)" & karst=="karst" ~ "600",
                             CharacteristicName=="Acid Neutralizing Capacity (ANC)" & karst=="non-karst" ~ "200",
                             CharacteristicName=="Total Nitrogen, mixed forms" & nutrient_ecoregion=="IX" ~ "0.69",
                             CharacteristicName=="Total Nitrogen, mixed forms" & nutrient_ecoregion=="XI" ~ "0.31",
                             CharacteristicName=="Total Phosphorus, mixed forms" & nutrient_ecoregion=="IX" ~ "0.037",
                             CharacteristicName=="Total Phosphorus, mixed forms" & nutrient_ecoregion=="XI" ~ "0.01",
                             CharacteristicName=="Dissolved oxygen (DO)" & cold_water=="warm" ~ "5.0",
                             CharacteristicName=="Dissolved oxygen (DO)" & cold_water=="cold" ~ "6.0",
                             CharacteristicName=="Salinity" ~ "0.5",
                             CharacteristicName=="Temperature, water" & cold_water=="warm" ~ "32",
                             CharacteristicName=="Temperature, water" & cold_water=="cold" ~ "20",
                             CharacteristicName=="pH"~"6–9")) %>%
  mutate(pass_fail=case_when(CharacteristicName=="Acid Neutralizing Capacity (ANC)" & karst=="karst" & ResultMeasureValue>600 ~ "P",
                             CharacteristicName=="Acid Neutralizing Capacity (ANC)" & karst=="non-karst" & ResultMeasureValue>200 ~ "P",
                             CharacteristicName=="Total Nitrogen, mixed forms" & nutrient_ecoregion=="IX" & ResultMeasureValue<0.69 ~ "P",
                             CharacteristicName=="Total Nitrogen, mixed forms" & nutrient_ecoregion=="XI" & ResultMeasureValue<0.31 ~ "P",
                             CharacteristicName=="Total Phosphorus, mixed forms" & nutrient_ecoregion=="IX" & ResultMeasureValue<0.037 ~ "P",
                             CharacteristicName=="Total Phosphorus, mixed forms" & nutrient_ecoregion=="XI" & ResultMeasureValue<0.01 ~ "P",
                             CharacteristicName=="pH" & (ResultMeasureValue<9 | ResultMeasureValue>6) ~ "P",
                             CharacteristicName=="Dissolved oxygen (DO)" & cold_water=="warm" & ResultMeasureValue>5.0 ~ "P",
                             CharacteristicName=="Dissolved oxygen (DO)" & cold_water=="cold" & ResultMeasureValue>6.0 ~ "P",
                             CharacteristicName=="Salinity" & ResultMeasureValue<0.5 ~ "P",
                             CharacteristicName=="Temperature, water" & cold_water=="warm" & ResultMeasureValue<32 ~ "P",
                             CharacteristicName=="Temperature, water" & cold_water=="cold" & ResultMeasureValue<20 ~ "P",
                             T ~ "F")) %>%
  mutate(CharacteristicName=case_when(CharacteristicName=="Acid Neutralizing Capacity (ANC)"~"Acid neutralizing capacity",
                                       CharacteristicName=="Dissolved oxygen (DO)"~"Dissolved oxygen",
                                       CharacteristicName=="Temperature, water"~"Water temperature",
                                       CharacteristicName=="Total Nitrogen, mixed forms"~"Total nitrogen",
                                       CharacteristicName=="Total Phosphorus, mixed forms"~"Total phosphorus",
                                       T~CharacteristicName)) %>%
  mutate(ParkName=case_when(Park=="ANTI"~"Antietam National Battlefield",
                             Park=="CATO"~"Catoctin Mountain Park",
                             Park=="GWMP"~"George Washington Memorial Parkway",
                             Park=="HAFE"~"Harpers Ferry National Historical Park",
                             Park=="MANA"~"Manassas National Battlefield Park",
                             Park=="MONO"~"Monocacy National Battlefield",
                             Park=="NACE"~"National Capital Parks-East",
                             Park=="PRWI"~"Prince William Forest Park",
                             Park=="ROCR"~"Rock Creek Park",
                             Park=="WOTR"~"Wolf Trap National Park for the Performing Arts")) %>%
  mutate(image=paste(Park, Site, sep="_")) %>%
  mutate(ResultMeasure.MeasureUnitCode=case_when(ResultMeasure.MeasureUnitCode=="deg C"~"\u00B0C",
                                                 ResultMeasure.MeasureUnitCode!="deg C"~ResultMeasure.MeasureUnitCode)) %>%
  select(ActivityStartDate, ParkName, MonitoringLocationName, cold_water, karst, CharacteristicName, ResultMeasureValue, ResultMeasure.MeasureUnitCode, year, threshold, pass_fail, image)

##changing column names
colnames(wq_data2) <- c("Date", "Park", "Site", "cold_water", "karst", "CharacteristicName",
                        "ResultMeasureValue", "unit", "year", "threshold", "pass_fail", "image")

```

```{r park wq data, include=F}
##filtering data frame by parameters
park_data <- wq_data2 %>%
  filter(Park==params$Park, Site==params$Site)

# park_data <- wq_data2 %>%
#   filter(Park=="Harpers Ferry National Historical Park", Site=="Flowing Springs Run")

##2024 data
park_data_24 <- park_data %>%
  filter(year==2024) %>%
  group_by(Site, CharacteristicName) %>%
  ##calculating percent pass
  mutate(percent_pass=(sum(pass_fail=="P")/sum(pass_fail=="P" | pass_fail=="F"))*100) %>%
  ##adding minimum and maximum value columns
  mutate(min=min(ResultMeasureValue),
         max=max(ResultMeasureValue)) %>%
  ##rounding to two decimal places in min and max columns
  mutate(min=round(min, digits=2),
         max=round(max, digits=2)) %>%
  group_by(Site, cold_water, karst, CharacteristicName, unit, threshold, min, max, percent_pass, image) %>%
  summarize()

##2019-23 data
park_data_19_23 <- park_data %>%
  filter(year!=2024) %>%
  group_by(Site, CharacteristicName) %>%
  mutate(percent_pass=(sum(pass_fail=="P")/sum(pass_fail=="P" | pass_fail=="F"))*100) %>%
  group_by(Site, CharacteristicName, percent_pass) %>%
  summarize()

```

```{r table df, include=F}
##merging 2024 and 2019-23 data frames 
table <- merge(park_data_24, park_data_19_23, by="CharacteristicName")

##creating data frame for table
table <- table %>%
  select(CharacteristicName, percent_pass.x, percent_pass.y) %>%
  ##rounding percent pass to two decimal places
  mutate(percent_pass.x=round(percent_pass.x, digits=0)) %>%
  mutate(percent_pass.y=round(percent_pass.y, digits=0)) %>%
  ##adding colors column based on percent pass
  mutate(colors1=if_else(percent_pass.x==100, "#ACE5EE", "#FE6F5E")) %>%
  mutate(colors2=if_else(percent_pass.y==100, "#ACE5EE", "#FE6F5E"))

##changing table column names
# colnames(table) = c("Parameter", "% passing 2024", "% passing 2019-23",
#                     "colors1", "colors2")

table2 <- table %>%
  # select(CharacteristicName, percent_pass.x, percent_pass.y) %>%
  pivot_longer(!(CharacteristicName | colors1 | colors2), names_to="years", values_to="percent_pass") %>%
  mutate(years=case_when(years=="percent_pass.x"~"2024",
                         years=="percent_pass.y"~"2019–23")) %>%
  mutate(colors=case_when(colors1=="#ACE5EE"~"black",
                          colors1=="#FE6F5E"~"#E32636")) %>%
  mutate(x_pos=case_when(CharacteristicName=="Acid neutralizing capacity"~1,
                         CharacteristicName=="Dissolved oxygen"~2,
                         CharacteristicName=="pH"~3,
                         CharacteristicName=="Salinity"~4,
                         CharacteristicName=="Total nitrogen"~5,
                         CharacteristicName=="Total phosphorus"~6,
                         CharacteristicName=="Water temperature"~7)) %>%
  select(CharacteristicName, x_pos, years, percent_pass, colors)

colnames(table2) = c("Parameter", "x_pos", "years", "percent_pass", "colors")

colors_list <- table2 %>%
  mutate(Parameter=case_when(Parameter=="pH"~"PH",
                             Parameter!="pH"~Parameter)) %>%
  group_by(Parameter, colors) %>%
  summarize() 

colors_list <- print(colors_list$colors)

```



<!-- COLUMN 1 -->

```{r table, echo=F, warning=F}
# kbl(table[,1:3], longtable=F) %>%
#   kable_paper() %>%
#   row_spec(0, color="black") %>%
#   column_spec(2, background=c(table$colors1)) %>%
#   column_spec(3, background=c(table$colors2))

```

```{r figure, echo=F}
bar_graph <- ggplot() +
  geom_bar(data=table2, aes(x=as.factor(x_pos), y=percent_pass, fill=years),
           width=0.7, color="black", size=0.8, position="dodge", stat="identity") +
  scale_fill_manual(name="Years", values=c("gray80", "#ACE5EE")) +
   scale_x_discrete(labels=c("Acid neutralizing\ncapacity", "Dissolved oxygen", "pH",
                             "Salinity", "Total nitrogen", "Total phosphorus", "Water temperature"))+
  geom_text(data=table2, aes(x=as.factor(x_pos), y=percent_pass, label=percent_pass, color=colors),
            position="dodge", vjust=-0.5, size=4) +
  xlab("Parameter") +
  ylab("Percent Passing") +
  coord_cartesian(xlim=c(0.3, 7.6), ylim=c(0, 107), expand=F) +
  theme_bw() +
  theme(axis.text.x=element_text(color=colors_list, angle=40, vjust=0.5))

bar_graph

```


```{r icons, include=F}
##creating function to print icons
# icon <- function(df) {
#   
#   if (df$pass_fail=="F") {
#     git_emoji("triangular_flag")
#     } else{print(" ")}
#   
# }

```

Acid Neutralizing Capacity (ANC)    
**Acceptable values:** Above `r park_data_24$threshold[park_data_24$CharacteristicName=="Acid neutralizing capacity"]` `r park_data_24$unit[park_data_24$CharacteristicName=="Acid neutralizing capacity"]`   
**2024 range:** `r park_data_24$min[park_data_24$CharacteristicName=="Acid neutralizing capacity"]` – `r park_data_24$max[park_data_24$CharacteristicName=="Acid neutralizing capacity"]` `r park_data_24$unit[park_data_24$CharacteristicName=="Acid neutralizing capacity"]`  
ANC is a measure of water’s ability to buffer acidic inputs. ANC measurements have never fallen below the acceptable threshold since monitoring began in 2005.  
   
Dissolved Oxygen (DO)  
**Acceptable values:** Above `r park_data_24$threshold[park_data_24$CharacteristicName=="Dissolved oxygen"]` `r park_data_24$unit[park_data_24$CharacteristicName=="Dissolved oxygen"]`  
**2024 range:** `r park_data_24$min[park_data_24$CharacteristicName=="Dissolved oxygen"]` – `r park_data_24$max[park_data_24$CharacteristicName=="Dissolved oxygen"]` `r park_data_24$unit[park_data_24$CharacteristicName=="Dissolved oxygen"]`   
Aquatic organisms rely on DO to survive. Cooler water holds more DO, so measurements vary by season. DO has not fallen below the acceptable threshold since 2006.  
  
pH  
**Acceptable range:** `r park_data_24$threshold[park_data_24$CharacteristicName=="pH"]`  
**2024 range:** `r park_data_24$min[park_data_24$CharacteristicName=="pH"]` – `r park_data_24$max[park_data_24$CharacteristicName=="pH"]`  
pH is a measure of how acidic or basic a liquid is.  pH measurements have fallen within the acceptable range since monitoring began in 2005.  
  
Salinity  
**Acceptable values:** Below `r park_data_24$threshold[park_data_24$CharacteristicName=="Salinity"]` `r park_data_24$unit[park_data_24$CharacteristicName=="Salinity"]`  
**2024 range:** `r park_data_24$min[park_data_24$CharacteristicName=="Salinity"]` – `r park_data_24$max[park_data_24$CharacteristicName=="Salinity"]` `r park_data_24$unit[park_data_24$CharacteristicName=="Salinity"]`  
Road salt is the main cause of high salinity in NCR streams.  Salinity has not surpassed the acceptable threshold at Flowing Springs Run since 2017.  
  
Total Nitrogen  
**Acceptable values:** Below `r park_data_24$threshold[park_data_24$CharacteristicName=="Total nitrogen"]` `r park_data_24$unit[park_data_24$CharacteristicName=="Total nitrogen"]`  
**2024 range:** `r park_data_24$min[park_data_24$CharacteristicName=="Total nitrogen"]` – `r park_data_24$max[park_data_24$CharacteristicName=="Total nitrogen"]` `r park_data_24$unit[park_data_24$CharacteristicName=="Total nitrogen"]`  
Nitrogen is commonly used in agricultural fertilizers. Under high concentrations, it can adversely affect aquatic life. All total nitrogen measurements since 2016 have exceeded the acceptable threshold.  
  
![](Site images\`r unique(park_data_24$image)`.png){width=300px}  
  
Total Phosphorus  
**Acceptable values:** Below `r park_data_24$threshold[park_data_24$CharacteristicName=="Total phosphorus"]` `r park_data_24$unit[park_data_24$CharacteristicName=="Total phosphorus"]`  
**2024 range:** `r park_data_24$min[park_data_24$CharacteristicName=="Total phosphorus"]` – `r park_data_24$max[park_data_24$CharacteristicName=="Total phosphorus"]` `r park_data_24$unit[park_data_24$CharacteristicName=="Total phosphorus"]`  
Phosphorus is often a limiting nutrient in freshwater streams, meaning a small increase in phosphorus concentration can lead to algal blooms. All observations in 2024 exceeded the threshold.  
  
Water Temperature  
**Acceptable values:** Below `r park_data_24$threshold[park_data_24$CharacteristicName=="Water temperature"]` `r park_data_24$unit[park_data_24$CharacteristicName=="Water temperature"]`  
**2024 range:** `r park_data_24$min[park_data_24$CharacteristicName=="Water temperature"]` – `r park_data_24$max[park_data_24$CharacteristicName=="Water temperature"]` `r park_data_24$unit[park_data_24$CharacteristicName=="Water temperature"]`   
Water temperature measurements have remained below the acceptable threshold since monitoring began in 2005.  
  
Water Quality Monitoring in the NCR  
Data on additional water quality parameters, including depth, discharge, conductivity, and total dissolved solids, are available in the [NCRN water quality data visualizer](https://irma.nps.gov/DataStore/Reference/Profile/2237386). Visit the [NCRN water quality monitoring webpage](https://www.nps.gov/im/ncrn/water.htm) to learn more.
