---
output: html_document
# output:
#   pagedown::html_paged:
#     self_contained: false
params:
  Park: "ROCR"
  Site: "BAKE"
  Year: "2025"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

```{r load packages, include=F}
##load packages
library(dplyr)
library(ggplot2)
source('R/ph_ex.R')
source('R/write_text.R')
```

```{r meta data, include=F}
metadata <- read.csv("wqp_ncrnwater_metadata.csv") %>%
  tidyr::separate(SiteCode, c("Network", "Park", "Site")) %>%
  ##changing Rock Creek at Dumbarton Oaks to Downstream of Dumbarton Oaks
  dplyr::mutate(SiteName=case_when(SiteName=="Rock Creek at Dumbarton Oaks"~"Rock Creek Downstream of Dumbarton Oaks",
                               TRUE~SiteName)) %>%
  ##creating column specifying karst v non-karst, cold vs warmwater, and nutrient ecoregion
  dplyr::mutate(karst=case_when(Park=="ANTI" | Park=="HAFE" | Park=="MONO" ~ "karst",
                         Park!="ANTI" | Park!="HAFE" | Park!="MONO" ~ "non-karst")) %>%
  dplyr::mutate(nutrient_ecoregion=case_when(Park=="ANTI" | Park=="CATO" | Park=="HAFE" ~ "XI",
                                      Park!="ANTI" | Park!="CATO" | Park!="HAFE" ~ "IX")) %>%
  dplyr::mutate(cold_water=case_when(Park=="CATO" ~ "coldwater",
                              Park!="CATO" ~ "warmwater")) 

##writing image alt text
image_info <- metadata %>%
  mutate(file_name=paste(Park, Site, sep="_")) %>%
  select(file_name) %>%
  distinct() %>%
  mutate(alt_text=case_when(file_name=="ANTI_SHCK"~"Leafy branches partially obscure a wide stream that runs under a concrete overpass.",
                            file_name=="CATO_BGHC"~"A wide stream filled with large rocks and surrounded by green trees.",
                            file_name=="CATO_BLBZ"~"A forest stream with rocky banks retreats under a fenced walking path.",
                            file_name=="CATO_OWCK"~"A stream filled with rocks and surrounded by grass and trees flows under a small bridge.",
                            file_name=="GWMP_MICR"~"A stream filled with large rocks and woody debris, and surrounded by leafy plants and bare trees flows under a tall bridge.",
                            file_name=="GWMP_MIRU"~"A wide, shallow stream filled with rocks and surrounded by standing and fallen trees flows under a road in the distance.",
                            file_name=="GWMP_PIRU"~"A stream filled with large rocks surrouned by green plants and trees.",
                            file_name=="GWMP_TURU"~"A stream, with rocky banks retreats into the distance.",
                            file_name=="HAFE_FLSP"~"A stream retreats into the distance in a lush green forest.",
                            file_name=="MANA_YOBR"~"A wide stream with muddy water retreats into the distance, with some bare tree trunks along its banks.",
                            file_name=="MONO_BUCK"~"A wide stream surrounded by a sloping, rocky bank on the left, a grassy bank on the right, and bare trees flows around a bend.",
                            file_name=="MONO_GAMI"~"A shallow stream with a pile of seidment in the middle surrounded by bare trees and patchy grass on the stream bank.",
                            file_name=="NACE_HECR"~"A wide stream surrounded by lush green shrubs and trees.",
                            file_name=="NACE_OXRU"~"A wide stream in an open field surrounded by grass on the left and tan pebbles on the right, with trees in the distance.",
                            file_name=="NACE_STCK"~"A small stream surrounded by sediment, pebbles, and grass on the right side, and plants and trees on the left side.",
                            file_name=="PRWI_BONE"~"A narrow stream surrounded by sparse bare trees, brown leaves on the ground, and some mosses on the stream bank.",
                            file_name=="PRWI_CARU"~"A narrow stream filled with sediment and surrounded by green plants. Multiple fallen or leaning trees lay across the stream.",
                            file_name=="PRWI_MARU"~"A narrow stream flows through a forest of trees with sparse or no leaves.",
                            file_name=="PRWI_MBBR"~"A narrow stream filled with rocks flows through a lush, green forest.",
                            file_name=="PRWI_NFQC"~"A wide stream surrounded by bare trees and some green plants flows around a bend.",
                            file_name=="PRWI_ORRU"~"A narrow stream surrounded by grass, dead leaves, and a bare tree flows into a small pond.",
                            file_name=="PRWI_SFQC"~"A wide stream surrounded by lush green trees",
                            file_name=="PRWI_SORU"~"A wide stream surrounded by bare trees and some shrubs.",
                            file_name=="PRWI_TARU"~"A shallow, narrow stream surrounded by green trees and plants flows into a culvert.",
                            file_name=="ROCR_BAKE"~"A shallow stream filled with rocks and surrounded by green trees.",
                            file_name=="ROCR_BRBR"~"A wide stream filled with rocks surrounded by a stone wall on the right, a hill on the left, and bare trees flows under a bridge road.",
                            file_name=="ROCR_DUOA"~"A narrow stream filled with rocks and woody debris, surrounded by a sandy and muddy stream bank, flows through a green forest.",
                            file_name=="ROCR_FEBR"~"A wide stream filled with rocks and surrounded by green plants and trees.",
                            file_name=="ROCR_KLVA"~"A rocky stream with a wall and fence to the right surrounded by lush green plants and trees.",
                            file_name=="ROCR_LUBR"~"A rocky stream surrounded by lush green plants and trees.",
                            file_name=="ROCR_NOST"~"A wide, rocky stream surrounded by trees with sparse or no leaves and fallen leaves on the ground flows under a small bridge.",
                            file_name=="ROCR_PHBR"~"A rocky sream surrounded by lush green plants and trees.",
                            file_name=="ROCR_PYBR"~"A rocky stream surrounded by lush green plants and trees flows under a tall, green bridge.",
                            file_name=="ROCR_R630"~"A rocky stream surrounded by lush green plants and trees.",
                            file_name=="ROCR_ROC3"~"A wide stream with large rocks surrounded by trees.",
                            file_name=="WOTR_CHCK"~"A wide stream runs through a forest of leaning green trees.",
                            file_name=="WOTR_WOTR"~"A wide stream surrounded by bare trees and some green plants and mosses.",
                            TRUE~""))




  
##filtering for park/site
park <- metadata %>%
  dplyr::filter(Park==params$Park & Site==params$Site)

##setting park, site, and year variables
mypark <- unique(park$LongName)
mysite <- unique(park$SiteName)

myyear <- params$Year

start_year <- (as.numeric(myyear))-5
end_year <- (as.numeric(myyear))-1
five_yr_range <- paste(as.character(start_year), as.character(end_year), sep="\U2013")

```

---
title: `r params$Year` Water Quality Summary
subtitle: "`r mypark`: `r mysite`"
--- 

<br>

```{css, echo=F}
img {vertical-align: top;}

p.caption {
width: 47%;
margin-left: 53%;
margin-right: 47%;
}

```

```{r wq data, include=F}
##creating data frame with exceedance thresholds
thresholds <- park %>%
  dplyr::select(DataName, LowerPoint, UpperPoint, Units, karst, 
                nutrient_ecoregion, cold_water) 

colnames(thresholds) <- c("CharacteristicName", "LowerPoint", "UpperPoint", "Units",
                          "karst", "nutrient_ecoregion", "cold_water")

##loading in water quality data
wq_data <- read.csv("wqp.csv")
# wq_data <- read.csv("wqp.csv") %>%
#   dplyr::mutate(MonitoringLocationName=case_when(MonitoringLocationName=="Battery Kemble Run"~"Battery Kemble Creek",
#                                                  TRUE~MonitoringLocationName))

##selecting columns
wq_data1 <- wq_data %>%
  dplyr::select(ActivityStartDate,
         MonitoringLocationName, CharacteristicName, 
         ResultMeasureValue) %>%
  dplyr::filter(MonitoringLocationName==mysite)

##converting date to date object
wq_data1$ActivityStartDate <- as.Date(wq_data1$ActivityStartDate, format = "%Y-%m-%d")

##extracting year
wq_data1$sample_year <- lubridate::year(wq_data1$ActivityStartDate)
wq_data1$sample_month <- lubridate::month(wq_data1$ActivityStartDate, label=T, abbr=F)
wq_data1$sample_my <- format(wq_data1$ActivityStartDate, "%B %Y")

##converting ResultMeasureValue to numeric object
wq_data1$ResultMeasureValue <- as.numeric(wq_data1$ResultMeasureValue) 

##removing NAs
wq_data1 <- wq_data1 %>%
  na.omit()

##merging wq and threshold data frames
wq_data_total <- merge(wq_data1, thresholds,
                        by=c("CharacteristicName"), all=T) %>%
  ##filtering for parameters of interest
  dplyr::filter(CharacteristicName %in% c("Acid Neutralizing Capacity (ANC)",
                                   "Total Nitrogen, mixed forms",
                                   "Total Phosphorus, mixed forms",
                                   "pH", "Dissolved oxygen (DO)",
                                   "Specific conductance", "Temperature, water")) %>%
  ##creating column with shortened parameter names for report
  dplyr::mutate(CharNameShort=case_when(CharacteristicName=="Acid Neutralizing Capacity (ANC)"~"ANC",
                                             CharacteristicName=="Dissolved oxygen (DO)"~"DO",
                                             CharacteristicName=="pH"~"pH",
                                             CharacteristicName=="Specific conductance"~"Specific conductance",
                                             CharacteristicName=="Temperature, water"~"Water temperature",
                                             CharacteristicName=="Total Nitrogen, mixed forms"~"Total nitrogen",
                                             CharacteristicName=="Total Phosphorus, mixed forms"~"Total phosphorus")) %>%
  ##creating column with lower case parameter names for report
  dplyr::mutate(CharNameLower=case_when(CharNameShort=="Specific conductance"~"specific conductance",
                                     CharNameShort=="Water temperature"~"water temperature",
                                     CharNameShort=="Total nitrogen"~"total nitrogen",
                                     CharNameShort=="Total phosphorus"~"total phosphorus",
                                     TRUE~CharNameShort)) %>%
  ##creating pass/fail column
  dplyr::mutate(pass_fail=case_when(ResultMeasureValue>=UpperPoint~"F",
                             ResultMeasureValue<=LowerPoint~"F",
                             TRUE~"P")) %>%
  ##calculating percent pass for each parameter per sampling year
  dplyr::group_by(CharacteristicName, sample_year) %>%
  dplyr::mutate(percent_pass=(sum(pass_fail=="P")/sum(pass_fail=="P" | pass_fail=="F"))*100) %>%
  dplyr::mutate(percent_pass=round(percent_pass, digits=0)) %>%
  ##creating pH exceedance column
  dplyr::mutate(pH_exceed=case_when(pass_fail=="F" & CharacteristicName=="pH" & ResultMeasureValue>9~"basic",
                                    pass_fail=="F" & CharacteristicName=="pH" & ResultMeasureValue<6~"acidic")) %>%
  ##finding maximum and minimum values for each parameter and sampling year
  dplyr::group_by(sample_year, CharacteristicName) %>%
  dplyr::mutate(min=min(ResultMeasureValue),
         max=max(ResultMeasureValue)) %>%
  ##rounding to two decimal places in min and max columns
  dplyr::mutate(min=case_when(CharNameShort=="Total phosphorus"~round(min, digits=3),
                              TRUE~round(min, digits=2)),
         max=case_when(CharNameShort=="Total phosphorus"~round(max, digits=3),
                              TRUE~round(max, digits=2)))


##changing column names
colnames(wq_data_total) <- c("CharacteristicName", "Date", "SiteName",
                             "ResultMeasureValue", "sample_year", "sample_month",
                             "month_year", "LowerPoint","UpperPoint", "unit",
                             "karst", "nutrient_ecoregion", "cold_water",
                             "CharNameShort", "CharNameLower", "pass_fail",
                             "percent_pass", "pH_exceed", "min", "max")

##creating data frame for current year + last 5 years
wq_data2 <- wq_data_total %>%
  dplyr::filter(sample_year>=start_year)

```

```{r park wq data, include=F}
## creating data frame for current data
park_data_current <- wq_data2 %>%
  dplyr::filter(sample_year==myyear) %>%
  ##filtering out unneeded columns 
  dplyr::select(-Date, -ResultMeasureValue, -sample_month, -month_year, 
                -pass_fail, -pH_exceed) %>%
  distinct() %>%
  ##creating column of text for parameters with percent pass between 1 and 99
  dplyr::mutate(major_P_F=case_when(percent_pass>50~paste("The majority of", CharNameLower, "measurements were acceptable at", mysite, "in", myyear, sep=" "),
                                    percent_pass<50 & percent_pass>0~paste("The majority of", CharNameLower, "measurements were not acceptable at", mysite, "in", myyear, sep=" "),
                                    percent_pass==50~paste("Half of", CharNameLower, "measurements were acceptable at", mysite, "in", myyear, sep=" ")))

##adding back pass_fail column 
park_data_current$pass_fail <- ifelse(park_data_current$percent_pass==100, "P", "F") 

##creating data frame for data from last 5 years
park_data_past <- wq_data2 %>%
  dplyr::filter(sample_year!=myyear) %>%
  dplyr::group_by(CharacteristicName) %>%
  dplyr::summarize(percent_pass=(sum(pass_fail=="P")/sum(pass_fail=="P" | pass_fail=="F"))*100) %>%
  dplyr::mutate(percent_pass=round(percent_pass, digits=0))

```

```{r merged df, include=F}
##merging current and past data frames 
park_merged_wide <- merge(park_data_current, park_data_past, by="CharacteristicName") %>%
  dplyr::select(CharacteristicName, CharNameShort, CharNameLower,
                percent_pass.x, major_P_F, percent_pass.y) 

##pivoting dataframe so that current and past data are different categories in the same column 
park_merged_long <- park_merged_wide %>%
  tidyr::pivot_longer(!(CharacteristicName | CharNameShort | CharNameLower | major_P_F), names_to="years", values_to="percent_pass") %>%
  ##changing year names
  dplyr::mutate(years=case_when(years=="percent_pass.x"~as.character(myyear),
                         years=="percent_pass.y"~five_yr_range)) %>%
  dplyr::mutate(colors=case_when(percent_pass==100~"black",
                          percent_pass!=100~"#E32636")) %>%
  ##assigning numbers to parameters for easy graphing
  dplyr::mutate(x_pos=case_when(CharacteristicName=="Acid Neutralizing Capacity (ANC)"~1,
                         CharacteristicName=="Dissolved oxygen (DO)"~2,
                         CharacteristicName=="pH"~3,
                         CharacteristicName=="Specific conductance"~4,
                         CharacteristicName=="Total Nitrogen, mixed forms"~5,
                         CharacteristicName=="Total Phosphorus, mixed forms"~6,
                         CharacteristicName=="Temperature, water"~7)) 

colnames(park_merged_long) = c("Parameter", "CharNameShort", "CharNameLower", "major_P_F", "years", "percent_pass", "colors", "x_pos")

```

```{r functions, echo=F, include=F, warning=F}
##function to find month and year of last exceedance
find_last_ex <- function(df, char) {
  
  print(unique(na.omit(df$month_year[df$Date==max(df$Date[df$pass_fail=="F" & df$CharNameShort==char])])))
      
}

##testing function 
find_last_ex(wq_data_total, "Total phosphorus")


##function to find month and year last passing measurement
find_last_pass <- function(df, char) {
  
  print(unique(na.omit(df$month_year[df$Date==max(df$Date[df$pass_fail=="P" & df$CharNameShort==char], na.rm=T)])))
  
}

##testing function
find_last_pass(wq_data_total, "Total phosphorus")


##function to find first year a parameter was recorded
find_first_year <- function(df, char) {
  
  print(min(df$sample_year[df$CharNameShort==char], na.rm=T))
  
}

##testing function
find_first_year(wq_data_total, "Total nitrogen")

```

```{r increase decrease, echo=F, include=F, warning=F}
##function to show increase/decrease in % pass and magnitude of change between past and current data 
increase_decrease <- function(df, char) {
  
  if(df$percent_pass.x[df$CharNameShort==char]-df$percent_pass.y[df$CharNameShort==char] >= 25) {
    print("increased considerably")
  } else if (df$percent_pass.x[df$CharNameShort==char]-df$percent_pass.y[df$CharNameShort==char] < 25 & df$percent_pass.x[df$CharNameShort==char]-df$percent_pass.y[df$CharNameShort==char] >= 10) {
    print("increased")
  } else if (df$percent_pass.x[df$CharNameShort==char]-df$percent_pass.y[df$CharNameShort==char] < 10 & df$percent_pass.x[df$CharNameShort==char]-df$percent_pass.y[df$CharNameShort==char] > 0) {
    print("increased slightly")
  } else if (df$percent_pass.x[df$CharNameShort==char]-df$percent_pass.y[df$CharNameShort==char] < 0 & df$percent_pass.x[df$CharNameShort==char]-df$percent_pass.y[df$CharNameShort==char] > -10) {
    print("decreased slightly")
  } else if (df$percent_pass.x[df$CharNameShort==char]-df$percent_pass.y[df$CharNameShort==char] <= -10 & df$percent_pass.x[df$CharNameShort==char]-df$percent_pass.y[df$CharNameShort==char] > -25) {
    print("decreased")
  } else if (df$percent_pass.x[df$CharNameShort==char]-df$percent_pass.y[df$CharNameShort==char] < -25) {
    print("decreased considerably")
  } else if (df$percent_pass.x[df$CharNameShort==char]==df$percent_pass.y[df$CharNameShort==char]) {
    print("remained the same")
  } 
  
}

##testing function
increase_decrease(park_merged_wide, "ANC")

```

```{r pH exceed, echo=F, include=F, warning=F}
##creating dataframe with only pH
pH_df <- wq_data_total[wq_data_total$CharacteristicName=="pH" & wq_data_total$sample_year>2018,]

##testing function
ph_ex(pH_df)

```

```{r text automation, echo=F, include=F, warning=F}
##statements:
##if 100% pass in current year and 5 years prior: text1
##if 0% pass in current year and 5 years prior: text3
##if 100% pass in current year but not before: text 2 + text 7
##if 0% pass in current year but not before: text 4 + text 7
##if neither 0 nor 100% pass in current year and changed from 5 years prior: text5
##if neither 0 nor 100% pass in current year and same value as 5 years prior: text 6



##testing function
write_text(wq_data_total, "Total phosphorus", park_merged_wide, park_merged_long)

```


```{r create figure, echo=F, warning=F}
##creating bar graph
bar_graph <- ggplot() +
  geom_bar(data=park_merged_long, aes(x=as.factor(x_pos), y=percent_pass, fill=years),
           width=0.7, color="black", size=0.8, position="dodge", stat="identity") +
  scale_fill_manual(name="Years", values=c("gray85", "#8DA0CB")) +
  scale_x_discrete(labels=c("Acid\nneutralizing\ncapacity", "Dissolved\noxygen", "pH",
                             "Specific\nconductance", "Total\nnitrogen", "Total\nphosphorus", "Water\ntemperature")) +
  coord_cartesian(xlim=c(0.3, 7.6), ylim=c(0, 110), expand=F) +
  geom_text(data=park_merged_long, aes(x=as.factor(x_pos), y=percent_pass + 3.5, group=years, label=percent_pass, color=colors),
            position=position_dodge2(width=0.7, preserve="total"), size=4) +
  scale_color_manual(values=c("#E32636", "black"), guide="none") +
  labs(title="Percent of Measurements Passing") +
  theme_bw() +
  theme(axis.text.x=element_text(color="black", size=11, angle=35, vjust=0.6, hjust=0.5),
        axis.text.y=element_text(size=11),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        legend.text=element_text(size=11),
        legend.title=element_blank(),
        legend.position=c(0.095, -0.30),
        legend.direction="horizontal",
        plot.title=element_text(size=18, face="bold"),
        plot.margin = unit(c(0,0.2,0.9,0), "cm"))

# bar_graph

##creating alt text for figure
fig_alt_text <- paste("A bar graph showing the percentage of passing measurements for seven water quality parameters at", mysite, "in", paste(mypark, ".", sep=""), "For each parameter, percentages of passing measurements are shown by two bars. Percent of passing measurements between", as.numeric(myyear)-5, "and", as.numeric(myyear)-1, "is shown by a gray bar on the left, while a blue bar on the right shows the percent of passing measurements in", paste(myyear, ".", sep=""), "The percentage of passing measurements for", as.numeric(myyear)-5, "through", as.numeric(myyear)-1, "and", paste(myyear, ",", sep=""), "respectively, are as follows for each parameter. Acid neutralizing capacity,", park_merged_long$percent_pass[park_merged_long$CharNameShort=="ANC" & park_merged_long$years==five_yr_range], "percent,", park_merged_long$percent_pass[park_merged_long$CharNameShort=="ANC" & park_merged_long$years==myyear], "percent.", "Dissolved oxygen,", park_merged_long$percent_pass[park_merged_long$CharNameShort=="DO" & park_merged_long$years==five_yr_range], "percent,", park_merged_long$percent_pass[park_merged_long$CharNameShort=="DO" & park_merged_long$years==myyear], "percent.", "PH,", park_merged_long$percent_pass[park_merged_long$CharNameShort=="pH" & park_merged_long$years==five_yr_range], "percent,", park_merged_long$percent_pass[park_merged_long$CharNameShort=="pH" & park_merged_long$years==myyear], "percent.", "Specific conductance,", park_merged_long$percent_pass[park_merged_long$CharNameShort=="Specific conductance" & park_merged_long$years==five_yr_range], "percent,", park_merged_long$percent_pass[park_merged_long$CharNameShort=="Specific conductance" & park_merged_long$years==myyear], "percent.", "Total nitrogen", park_merged_long$percent_pass[park_merged_long$CharNameShort=="Total nitrogen" & park_merged_long$years==five_yr_range], "percent,", park_merged_long$percent_pass[park_merged_long$CharNameShort=="Total nitrogen" & park_merged_long$years==myyear], "percent.", "Total phosphorus,", park_merged_long$percent_pass[park_merged_long$CharNameShort=="Total phosphorus" & park_merged_long$years==five_yr_range], "percent,", park_merged_long$percent_pass[park_merged_long$CharNameShort=="Total phosphorus" & park_merged_long$years==myyear], "percent.", "Water temperature,", park_merged_long$percent_pass[park_merged_long$CharNameShort=="Water temperature" & park_merged_long$years==five_yr_range], "percent,", park_merged_long$percent_pass[park_merged_long$CharNameShort=="Water temperature" & park_merged_long$years==myyear], "percent.", sep=" ")

```

```{r setting up site photo, echo=F}
##setting image name
fig_name <- paste(unique(park$Park), unique(park$Site), sep="_")

##setting image file path
file_path <- paste("Site images/", fig_name, ".png", sep="")

##creating object to print image
site_image <- knitr::include_graphics(file_path)

##pulling alt text from image_info dataframe
img_alt_text <- image_info$alt_text[image_info$file_name==fig_name]

```

```{r figure and photo, echo=F, fig.show="hold", out.width=c("53%", "47%"), fig.alt = c(fig_alt_text, img_alt_text), fig.cap=paste(mysite, "is a", unique(park_data_current$cold_water), unique(park_data_current$karst), "stream.", sep=" ")}
par(mar = c(4, 4, .1, .1))

bar_graph

site_image

```


<br>
  
`r Rmoji::git_emoji("triangular_flag")` Red flags indicate parameters that exceeded the acceptable threshold at least once in 2025.
<br>
  
<!-- starting 2 column format -->
:::::::::::::: {.columns}

<!-- COLUMN 1 -->
::: {.column width="47.5%"}
  
```{r icons, include=F}
##creating function to print icons
icon <- function(df) {
  
  if (df$pass_fail=="F") {
    Rmoji::git_emoji("triangular_flag")
    } else{print(" ")}
  
}

```

##### **Acid Neutralizing Capacity (ANC)** `r icon(park_data_current[park_data_current$CharacteristicName=="Acid Neutralizing Capacity (ANC)",])`       
**Acceptable values:** Above `r park_data_current$LowerPoint[park_data_current$CharacteristicName=="Acid Neutralizing Capacity (ANC)"]` `r park_data_current$unit[park_data_current$CharacteristicName=="Acid Neutralizing Capacity (ANC)"]`   
**`r myyear` range:** `r park_data_current$min[park_data_current$CharacteristicName=="Acid Neutralizing Capacity (ANC)"]` – `r park_data_current$max[park_data_current$CharacteristicName=="Acid Neutralizing Capacity (ANC)"]` `r park_data_current$unit[park_data_current$CharacteristicName=="Acid Neutralizing Capacity (ANC)"]`  
`r write_text(wq_data_total, "ANC", park_merged_wide, park_merged_long)`  
<br>
  
##### **Dissolved Oxygen (DO)** `r icon(park_data_current[park_data_current$CharacteristicName=="Dissolved oxygen (DO)",])`    
**Acceptable values:** Above `r park_data_current$LowerPoint[park_data_current$CharacteristicName=="Dissolved oxygen (DO)"]` `r park_data_current$unit[park_data_current$CharacteristicName=="Dissolved oxygen (DO)"]`  
**`r myyear` range:** `r park_data_current$min[park_data_current$CharacteristicName=="Dissolved oxygen (DO)"]` – `r park_data_current$max[park_data_current$CharacteristicName=="Dissolved oxygen (DO)"]` `r park_data_current$unit[park_data_current$CharacteristicName=="Dissolved oxygen (DO)"]`   
`r write_text(wq_data_total, "DO", park_merged_wide, park_merged_long)`  
<br>
  
##### **pH** `r icon(park_data_current[park_data_current$CharacteristicName=="pH",])`    
**Acceptable range:** `r park_data_current$LowerPoint[park_data_current$CharacteristicName=="pH"]` – `r park_data_current$UpperPoint[park_data_current$CharacteristicName=="pH"]`    
**`r myyear` range:** `r park_data_current$min[park_data_current$CharacteristicName=="pH"]` – `r park_data_current$max[park_data_current$CharacteristicName=="pH"]`  
`r write_text(wq_data_total, "pH", park_merged_wide, park_merged_long)` `r ph_ex(pH_df)`  
<br>
  
##### **Specific Conductance** `r icon(park_data_current[park_data_current$CharacteristicName=="Specific conductance",])`    
**Acceptable values:** Below `r park_data_current$UpperPoint[park_data_current$CharacteristicName=="Specific conductance"]` `r park_data_current$unit[park_data_current$CharacteristicName=="Specific conductance"]`  
**`r myyear` range:** `r park_data_current$min[park_data_current$CharacteristicName=="Specific conductance"]` – `r park_data_current$max[park_data_current$CharacteristicName=="Specific conductance"]` `r park_data_current$unit[park_data_current$CharacteristicName=="Specific conductance"]`  
`r write_text(wq_data_total, "Specific conductance", park_merged_wide, park_merged_long)`  

:::

::: {.column width="5%"}
<!-- blank space -->
:::

<!-- COLUMN 2 -->
::: {.column width="47.5%"}

##### **Total Nitrogen** `r icon(park_data_current[park_data_current$CharacteristicName=="Total Nitrogen, mixed forms",])`   
**Acceptable values:** Below `r park_data_current$UpperPoint[park_data_current$CharacteristicName=="Total Nitrogen, mixed forms"]` `r park_data_current$unit[park_data_current$CharacteristicName=="Total Nitrogen, mixed forms"]`  
**`r myyear` range:** `r park_data_current$min[park_data_current$CharacteristicName=="Total Nitrogen, mixed forms"]` – `r park_data_current$max[park_data_current$CharacteristicName=="Total Nitrogen, mixed forms"]` `r park_data_current$unit[park_data_current$CharacteristicName=="Total Nitrogen, mixed forms"]`  
`r write_text(wq_data_total, "Total nitrogen", park_merged_wide, park_merged_long)`  
<br>
  
##### **Total Phosphorus** `r icon(park_data_current[park_data_current$CharacteristicName=="Total Phosphorus, mixed forms",])`  
**Acceptable values:** Below `r park_data_current$UpperPoint[park_data_current$CharacteristicName=="Total Phosphorus, mixed forms"]` `r park_data_current$unit[park_data_current$CharacteristicName=="Total Phosphorus, mixed forms"]`  
**`r myyear` range:** `r park_data_current$min[park_data_current$CharacteristicName=="Total Phosphorus, mixed forms"]` – `r park_data_current$max[park_data_current$CharacteristicName=="Total Phosphorus, mixed forms"]` `r park_data_current$unit[park_data_current$CharacteristicName=="Total Phosphorus, mixed forms"]`  
`r write_text(wq_data_total, "Total phosphorus", park_merged_wide, park_merged_long)`.  
<br>
  
##### **Water Temperature**`r icon(park_data_current[park_data_current$CharacteristicName=="Temperature, water",])`    
**Acceptable values:** Below `r park_data_current$UpperPoint[park_data_current$CharacteristicName=="Temperature, water"]` `r park_data_current$unit[park_data_current$CharacteristicName=="Temperature, water"]`  
**`r myyear` range:** `r park_data_current$min[park_data_current$CharacteristicName=="Temperature, water"]` – `r park_data_current$max[park_data_current$CharacteristicName=="Temperature, water"]` `r park_data_current$unit[park_data_current$CharacteristicName=="Temperature, water"]`   
`r write_text(wq_data_total, "Water temperature", park_merged_wide, park_merged_long)`  
<br>
    
##### **Water Quality Monitoring in the NCR**  
This report summarizes water quality data from `r start_year` to `r myyear` for seven parameters. The National Capital Region Inventory & Monitoring Network (NCRN I&M) monitors additional water quality parameters, including depth, discharge, conductivity, and total dissolved solids. These data are available in the [NCRN I\&M water quality data visualizer](https://irma.nps.gov/DataStore/Reference/Profile/2237386). Visit the [NCRN I&M water quality monitoring webpage](https://www.nps.gov/im/ncrn/water.htm) to learn more. 

:::

::::::::::::::
  
  
<font size="3">A **printable PDF version** of this page is available in the **[NPS DataStore](https://irma.nps.gov/DataStore/Reference/Profile/2316392)**.</font>
<br>
<br>



