---
title: |
  | `r params$Year` Water Quality Annual Summary: 
  | `r params$Park`, `r params$Site`
output: pdf_document
params:
  Park: "Prince William Forest Park"
  Site: "Orenda Run"
  Year: "2024"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load packages, include=F}
##load packages
library(tinytex)
library(shiny)
library(tidyr)
library(dplyr)
library(ggplot2)
library(lubridate)
library(knitr)
#install.packages("kableExtra")
library(kableExtra)
#install.packages("Rmoji")
library(Rmoji)
#install.packages("plotly")
library(plotly)
library(ggplot2)

```

```{r wq data, include=F}
##loading in data
current_wd <- getwd()
setwd(current_wd)
wq_data <- read.csv("wqp.csv")

##selecting columns
wq_data1 <- wq_data[, c("ActivityStartDate", "MonitoringLocationIdentifier",
                       "MonitoringLocationName", "CharacteristicName", 
                       "ResultMeasureValue", "ResultMeasure.MeasureUnitCode")]

##converting date to date object
wq_data1$ActivityStartDate <- as.Date(wq_data1$ActivityStartDate, format = "%Y-%m-%d")
##extracting year
wq_data1$year <- year(wq_data1$ActivityStartDate)

##converting ResultMeasureValue to numeric object
wq_data1$ResultMeasureValue <- as.numeric(wq_data1$ResultMeasureValue)

##data wrangling
wq_data2 <- wq_data1 %>%
  na.omit() %>%
  filter(CharacteristicName %in% c("Acid Neutralizing Capacity (ANC)",
                                   "Total Nitrogen, mixed forms",
                                   "Total Phosphorus, mixed forms",
                                   "pH", "Dissolved oxygen (DO)",
                                   "Salinity", "Temperature, water")) %>%
  filter(year>2018) %>%
  separate(MonitoringLocationIdentifier, c("Network", "Park", "Site")) %>%
  select(ActivityStartDate, Park, Site, MonitoringLocationName, CharacteristicName, ResultMeasureValue, ResultMeasure.MeasureUnitCode, year) %>%
  mutate(karst=case_when(Park=="ANTI" | Park=="HAFE" | Park=="MONO" ~ "karst",
                         Park!="ANTI" | Park!="HAFE" | Park!="MONO" ~ "non-karst")) %>%
  mutate(nutrient_ecoregion=case_when(Park=="ANTI" | Park=="CATO" | Park=="HAFE" ~ "XI",
                                      Park!="ANTI" | Park!="CATO" | Park!="HAFE" ~ "IX")) %>%
  mutate(cold_water=case_when(Park=="CATO" ~ "cold",
                              Park!="CATO" ~ "warm")) %>%
  mutate(threshold=case_when(CharacteristicName=="Acid Neutralizing Capacity (ANC)" & karst=="karst" ~ "600",
                             CharacteristicName=="Acid Neutralizing Capacity (ANC)" & karst=="non-karst" ~ "200",
                             CharacteristicName=="Total Nitrogen, mixed forms" & nutrient_ecoregion=="IX" ~ "0.69",
                             CharacteristicName=="Total Nitrogen, mixed forms" & nutrient_ecoregion=="XI" ~ "0.31",
                             CharacteristicName=="Total Phosphorus, mixed forms" & nutrient_ecoregion=="IX" ~ "0.037",
                             CharacteristicName=="Total Phosphorus, mixed forms" & nutrient_ecoregion=="XI" ~ "0.01",
                             CharacteristicName=="Dissolved oxygen (DO)" & cold_water=="warm" ~ "5.0",
                             CharacteristicName=="Dissolved oxygen (DO)" & cold_water=="cold" ~ "6.0",
                             CharacteristicName=="Salinity" ~ "0.5",
                             CharacteristicName=="Temperature, water" & cold_water=="warm" ~ "32",
                             CharacteristicName=="Temperature, water" & cold_water=="cold" ~ "20",
                             CharacteristicName=="pH"~"6–9")) %>%
  mutate(pass_fail=case_when(CharacteristicName=="Acid Neutralizing Capacity (ANC)" & karst=="karst" & ResultMeasureValue>600 ~ "P",
                             CharacteristicName=="Acid Neutralizing Capacity (ANC)" & karst=="non-karst" & ResultMeasureValue>200 ~ "P",
                             CharacteristicName=="Total Nitrogen, mixed forms" & nutrient_ecoregion=="IX" & ResultMeasureValue<0.69 ~ "P",
                             CharacteristicName=="Total Nitrogen, mixed forms" & nutrient_ecoregion=="XI" & ResultMeasureValue<0.31 ~ "P",
                             CharacteristicName=="Total Phosphorus, mixed forms" & nutrient_ecoregion=="IX" & ResultMeasureValue<0.037 ~ "P",
                             CharacteristicName=="Total Phosphorus, mixed forms" & nutrient_ecoregion=="XI" & ResultMeasureValue<0.01 ~ "P",
                             CharacteristicName=="pH" & (ResultMeasureValue<9 | ResultMeasureValue>6) ~ "P",
                             CharacteristicName=="Dissolved oxygen (DO)" & cold_water=="warm" & ResultMeasureValue>5.0 ~ "P",
                             CharacteristicName=="Dissolved oxygen (DO)" & cold_water=="cold" & ResultMeasureValue>6.0 ~ "P",
                             CharacteristicName=="Salinity" & ResultMeasureValue<0.5 ~ "P",
                             CharacteristicName=="Temperature, water" & cold_water=="warm" & ResultMeasureValue<32 ~ "P",
                             CharacteristicName=="Temperature, water" & cold_water=="cold" & ResultMeasureValue<20 ~ "P",
                             T ~ "F")) %>%
  mutate(CharacteristicName=case_when(CharacteristicName=="Acid Neutralizing Capacity (ANC)"~"Acid neutralizing capacity",
                                       CharacteristicName=="Dissolved oxygen (DO)"~"Dissolved oxygen",
                                       CharacteristicName=="Temperature, water"~"Water temperature",
                                       CharacteristicName=="Total Nitrogen, mixed forms"~"Total nitrogen",
                                       CharacteristicName=="Total Phosphorus, mixed forms"~"Total phosphorus",
                                       T~CharacteristicName)) %>%
  mutate(ParkName=case_when(Park=="ANTI"~"Antietam National Battlefield",
                             Park=="CATO"~"Catoctin Mountain Park",
                             Park=="GWMP"~"George Washington Memorial Parkway",
                             Park=="HAFE"~"Harpers Ferry National Historical Park",
                             Park=="MANA"~"Manassas National Battlefield Park",
                             Park=="MONO"~"Monocacy National Battlefield",
                             Park=="NACE"~"National Capital Parks-East",
                             Park=="PRWI"~"Prince William Forest Park",
                             Park=="ROCR"~"Rock Creek Park",
                             Park=="WOTR"~"Wolf Trap National Park for the Performing Arts")) %>%
  mutate(image=paste(Park, Site, sep="_")) %>%
  mutate(ResultMeasure.MeasureUnitCode=case_when(ResultMeasure.MeasureUnitCode=="deg C"~"\u00B0C",
                                                 ResultMeasure.MeasureUnitCode!="deg C"~ResultMeasure.MeasureUnitCode)) %>%
  select(ActivityStartDate, ParkName, MonitoringLocationName, cold_water, karst, CharacteristicName, ResultMeasureValue, ResultMeasure.MeasureUnitCode, year, threshold, pass_fail, image)

##changing column names
colnames(wq_data2) <- c("Date", "Park", "Site", "cold_water", "karst", "CharacteristicName",
                        "ResultMeasureValue", "unit", "year", "threshold", "pass_fail", "image")

```

```{r park wq data, include=F}
##filtering data frame by parameters
park_data <- wq_data2 %>%
  filter(Park==params$Park, Site==params$Site)

# park_data <- wq_data2 %>%
#   filter(Park=="Prince William Forest Park", Site=="Orenda Run")

##2024 data
park_data_24 <- park_data %>%
  filter(year==2024) %>%
  group_by(Site, CharacteristicName) %>%
  ##calculating percent pass
  mutate(percent_pass=(sum(pass_fail=="P")/sum(pass_fail=="P" | pass_fail=="F"))*100) %>%
  ##adding minimum and maximum value columns
  mutate(min=min(ResultMeasureValue),
         max=max(ResultMeasureValue)) %>%
  ##rounding to two decimal places in min and max columns
  mutate(min=round(min, digits=2),
         max=round(max, digits=2)) %>%
  group_by(Site, cold_water, karst, CharacteristicName, unit, threshold, min, max, pass_fail, percent_pass, image) %>%
  summarize()

##function to remove duplicate rows for parameters with both passing and failing values 
remove_duplicates <- function(df) {
  
  if (nrow(df[df$CharacteristicName=="Acid neutralizing capacity",])==2) {
  df <- df[!(df$CharacteristicName=="Acid neutralizing capacity" & df$pass_fail=="P"),]
  } else{df <- df}
  
  if (nrow(df[df$CharacteristicName=="Dissolved oxygen",])==2) {
  df <- df[!(df$CharacteristicName=="Dissolved oxygen" & df$pass_fail=="P"),]
  } else{df <- df}

  if (nrow(df[df$CharacteristicName=="Salinity",])==2) {
  df <- df[!(df$CharacteristicName=="Salinity" & df$pass_fail=="P"),]
  } else{df <- df}

  if (nrow(df[df$CharacteristicName=="Total nitrogen",])==2) {
  df <- df[!(df$CharacteristicName=="Total nitrogen" & df$pass_fail=="P"),]
  } else{df <- df}

  if (nrow(df[df$CharacteristicName=="Total phosphorus",])==2) {
  df <- df[!(df$CharacteristicName=="Total phosphorus" & df$pass_fail=="P"),]
  } else{df <- df}

  if (nrow(df[df$CharacteristicName=="Water temperature",])==2) {
  df <- df[!(df$CharacteristicName=="Water temperature" & df$pass_fail=="P"),]
  } else{df <- df}
  
}

park_data_24 <- remove_duplicates(park_data_24)

##2019-23 data
park_data_19_23 <- park_data %>%
  filter(year!=2024) %>%
  group_by(Site, CharacteristicName) %>%
  mutate(percent_pass=(sum(pass_fail=="P")/sum(pass_fail=="P" | pass_fail=="F"))*100) %>%
  group_by(Site, CharacteristicName, percent_pass) %>%
  summarize()

```

<!--setting up data frame for table and figures-->
```{r table df, include=F}
##merging 2024 and 2019-23 data frames 
table <- merge(park_data_24, park_data_19_23, by="CharacteristicName")

##creating data frame for table
table <- table %>%
  select(CharacteristicName, percent_pass.x, percent_pass.y) %>%
  ##rounding percent pass to two decimal places
  mutate(percent_pass.x=round(percent_pass.x, digits=0)) %>%
  mutate(percent_pass.y=round(percent_pass.y, digits=0)) 
  ##adding colors column based on percent pass
  # mutate(colors1=if_else(percent_pass.x==100, "#ACE5EE", "#FE6F5E")) %>%
  # mutate(colors2=if_else(percent_pass.y==100, "#ACE5EE", "#FE6F5E"))

##changing table column names
# colnames(table) = c("Parameter", "% passing 2024", "% passing 2019-23",
#                     "colors1", "colors2")

table2 <- table %>%
  pivot_longer(!(CharacteristicName), names_to="years", values_to="percent_pass") %>%
  mutate(years=case_when(years=="percent_pass.x"~"2024",
                         years=="percent_pass.y"~"2019–23")) %>%
  mutate(colors=case_when(percent_pass==100~"black",
                          percent_pass!=100~"#E32636")) %>%
  mutate(x_pos=case_when(CharacteristicName=="Acid neutralizing capacity"~1,
                         CharacteristicName=="Dissolved oxygen"~2,
                         CharacteristicName=="pH"~3,
                         CharacteristicName=="Salinity"~4,
                         CharacteristicName=="Total nitrogen"~5,
                         CharacteristicName=="Total phosphorus"~6,
                         CharacteristicName=="Water temperature"~7)) %>%
  select(CharacteristicName, x_pos, years, percent_pass, colors)

colnames(table2) = c("Parameter", "x_pos", "years", "percent_pass", "colors")

colors_list <- table2 %>%
  mutate(Parameter=case_when(Parameter=="pH"~"PH",
                             Parameter!="pH"~Parameter)) %>%
  group_by(Parameter, colors, years) %>%
  summarize() 

##function  
# color_list <- function(df) {
#   
#   if (nrow(df[(df$Parameter=="Acid neutralizing capacity" & colors_list$colors=="black"),])==2) {
#   df <- df[!(df$CharacteristicName=="Acid neutralizing capacity" & df$years=="2019–23"),]
#   } else{df <- df}
#   
# }

colors_list <- print(colors_list$colors)

```

<!--% pass table-->
```{r table, echo=F, warning=F}
# kbl(table[,1:3], longtable=F) %>%
#   kable_paper() %>%
#   row_spec(0, color="black") %>%
#   column_spec(2, background=c(table$colors1)) %>%
#   column_spec(3, background=c(table$colors2))

```

<!--creating figure-->
```{r figure, echo=F, warning=F, fig.width = 5, fig.height = 4}
##creating bar graph
# bar_graph <- ggplot() +
#   geom_bar(data=table2, aes(x=as.factor(x_pos), y=percent_pass, fill=years),
#            width=0.7, color="black", size=0.8, position="dodge", stat="identity") +
#   scale_fill_manual(name="Years", values=c("gray85", "#8DA0CB")) +
#   scale_x_discrete(labels=c("Acid\nneutralizing\ncapacity", "Dissolved\noxygen", "pH",
#                              "Salinity", "Total\nnitrogen", "Total\nphosphorus", "Water\ntemperature")) +
#   xlab("Parameter") +
#   ylab("% Passing") +
#   coord_cartesian(xlim=c(0.3, 7.6), ylim=c(0, 110), expand=F) +
#   # geom_text(data=table2, aes(x=as.factor(x_pos), y=percent_pass + 3.5, group=years, label=percent_pass, color=colors),
#   #           position=position_dodge2(width=0.7, preserve="total"), size=2.5) +
#   geom_text(data=table2, aes(x=as.factor(x_pos), y=percent_pass + 3.5, group=years, label=percent_pass, color=colors),
#             position=position_dodge2(width=0.7, preserve="total"), size=2.5) +
#   scale_color_manual(values=c("#E32636", "black"), guide="none") +
#   theme_bw() +
#   theme(axis.text.x=element_text(color=colors_list, size=8, angle=35, vjust=0.8, hjust=0.5),
#         axis.title.x=element_text(vjust=3),
#         legend.position=c(0.15, -0.4),
#         legend.direction="horizontal",
#         plot.margin = unit(c(1,1,1,1), "cm"))
# 
# bar_graph

```

```{r, include=F}
# bar_graph <- ggplot() +
#   geom_bar(data=table2, aes(x=as.factor(x_pos), y=percent_pass, fill=years),
#            width=0.7, color="black", position="dodge", stat="identity") +
#   scale_fill_manual(name="Years", values=c("gray85", "#8DA0CB")) +
#   scale_x_discrete(labels=c("Acid neutralizing\ncapacity", "Dissolved oxygen", "pH",
#                              "Salinity", "Total nitrogen", "Total phosphorus", "Water temperature")) +
#   xlab("Parameter") +
#   ylab("% Passing") +
#   coord_cartesian(xlim=c(0.3, 7.6), ylim=c(0, 107), expand=F) +
#   geom_text(data=table2, aes(x=as.factor(x_pos), y=percent_pass + 3.5, group=years, label=percent_pass, color=colors),
#             position=position_dodge2(width=0.7, preserve="total"), size=3) +
#   scale_color_manual(values=c("#E32636", "black"), guide="none") +
#   theme_bw() +
#   theme(axis.text.x=element_text(color=colors_list, angle=40, vjust=0.5, hjust=0.5))
# 
# #bar_graph
# 
# ggplotly(bar_graph)

```

```{r plotly graph, echo=F, warning=F}
##editing table df
table3 <- table %>%
  select(CharacteristicName, percent_pass.x, percent_pass.y) %>%
  mutate(colors=case_when(percent_pass.x==100~"black",
                          percent_pass.x!=100~"#E32636")) %>%
  mutate(CharacteristicName=case_when(CharacteristicName=="Acid neutralizing capacity"~"Acid\nneutralizing\ncapacity",
                                      CharacteristicName=="Dissolved oxygen"~"Dissolved\noxygen",
                                      CharacteristicName=="Total nitrogen"~"Total\nnitrogen",
                                      CharacteristicName=="Total phosphorus"~"Total\nphosphorus",
                                      CharacteristicName=="Water temperature"~"Water\ntemperature",
                                      T~CharacteristicName))

colnames(table3) <- c("CharacteristicName", "current", "prev", "colors")

##making bar graph in plotly
bar_graph <- plot_ly(table3, x=~CharacteristicName, y=~prev,
                     type="bar", name="2019–23",
                     text=~prev, textposition="auto",
                     marker=list(color="#D9D9D9",
                                 line=list(color="black",
                                           width = 1.5)))
bar_graph <- bar_graph %>%
  add_trace(y=~current, name="2024",
            text=~current, textposition="auto",
            marker=list(color="#8DA0CB",
                        line=list(color="black",
                                  width = 1.5))) %>%
  layout(yaxis=list(title="% Passing"),
         xaxis=list(title="Parameter", standoff=50,  showticklabels=F),
         barmode="group", margin=list(t=50, b=75, l=75, r=50)) %>%
  add_annotations(x=table3$CharacteristicName[1], y=-0.25,
                  xref="x", yref="paper",
                  text=table3$CharacteristicName[1],
                  font=list(color=table3$colors[1], size=10),
                  textangle=-30,
                  showarrow=F) %>%
  add_annotations(x=table3$CharacteristicName[2], y=-0.25,
                  xref="x", yref="paper",
                  text=table3$CharacteristicName[2],
                  font=list(color=table3$colors[2], size=10),
                  textangle=-30,
                  showarrow=F) %>%
  add_annotations(x=table3$CharacteristicName[3], y=-0.25,
                  xref="x", yref="paper",
                  text=table3$CharacteristicName[3],
                  font=list(color=table3$colors[3], size=10),
                  textangle=-30,
                  showarrow=F) %>%
  add_annotations(x=table3$CharacteristicName[4], y=-0.25,
                  xref="x", yref="paper",
                  text=table3$CharacteristicName[4],
                  font=list(color=table3$colors[4], size=10),
                  textangle=-30,
                  showarrow=F) %>%
  add_annotations(x=table3$CharacteristicName[5], y=-0.25,
                  xref="x", yref="paper",
                  text=table3$CharacteristicName[5],
                  font=list(color=table3$colors[5], size=10),
                  textangle=-30,
                  showarrow=F) %>%
  add_annotations(x=table3$CharacteristicName[6], y=-0.25,
                  xref="x", yref="paper",
                  text=table3$CharacteristicName[6],
                  font=list(color=table3$colors[6], size=10),
                  textangle=-30,
                  showarrow=F) %>%
  add_annotations(x=table3$CharacteristicName[7], y=-0.25,
                  xref="x", yref="paper",
                  text=table3$CharacteristicName[7],
                  font=list(color=table3$colors[7], size=10),
                  textangle=-30,
                  showarrow=F)

bar_graph


  # add_annotations(x=-0.1, y=c(0, 20, 40, 60, 80, 100),
  #                 xref="paper", yref="y",
  #                 text=c("0", "20", "40", "60", "80", "100"),
  #                 font=list(color="black"),
  #                 showarrow=F)


# kaleido(bar_graph, "bar_graph.pdf")

```

![](Site images\`r unique(park_data_24$image)`.png){width=200px}
<!--![](Site images\maps\`r unique(park_data_24$image)`_map2.png){width=200px}-->

<!--function for adding icons to parameters with exceedances-->
```{r icons, include=F}
##creating function to print icons
icon <- function(df) {

  if (df$pass_fail=="F") {
    #git_emoji("triangular_flag")
    "!"
    } else{print(" ")}

}

```

<!--start two column format-->
```{r, echo=F, results="asis"}

cat("\\twocolumn")

```

Acid Neutralizing Capacity (ANC) \textbf{\textcolor{red}{`r icon(park_data_24[park_data_24$CharacteristicName=="Acid neutralizing capacity",])`}}        
**Acceptable values:** Above `r park_data_24$threshold[park_data_24$CharacteristicName=="Acid neutralizing capacity"]` `r park_data_24$unit[park_data_24$CharacteristicName=="Acid neutralizing capacity"]`   
**2024 range:** `r park_data_24$min[park_data_24$CharacteristicName=="Acid neutralizing capacity"]` – `r park_data_24$max[park_data_24$CharacteristicName=="Acid neutralizing capacity"]` `r park_data_24$unit[park_data_24$CharacteristicName=="Acid neutralizing capacity"]`  
ANC is a measure of water’s ability to buffer acidic inputs. ANC measurements have never fallen below the acceptable threshold since monitoring began in 2005.   
   
Dissolved Oxygen (DO) \textbf{\textcolor{red}{`r icon(park_data_24[park_data_24$CharacteristicName=="Dissolved oxygen",])`}}    
**Acceptable values:** Above `r park_data_24$threshold[park_data_24$CharacteristicName=="Dissolved oxygen"]` `r park_data_24$unit[park_data_24$CharacteristicName=="Dissolved oxygen"]`  
**2024 range:** `r park_data_24$min[park_data_24$CharacteristicName=="Dissolved oxygen"]` – `r park_data_24$max[park_data_24$CharacteristicName=="Dissolved oxygen"]` `r park_data_24$unit[park_data_24$CharacteristicName=="Dissolved oxygen"]`   
Aquatic organisms rely on DO to survive. Cooler water holds more DO, so measurements vary by season. DO has not fallen below the acceptable threshold since 2006.  
  
pH \textbf{\textcolor{red}{`r icon(park_data_24[park_data_24$CharacteristicName=="pH",])`}}    
**Acceptable range:** `r park_data_24$threshold[park_data_24$CharacteristicName=="pH"]`  
**2024 range:** `r park_data_24$min[park_data_24$CharacteristicName=="pH"]` – `r park_data_24$max[park_data_24$CharacteristicName=="pH"]`  
pH is a measure of how acidic or basic a liquid is.  pH measurements have fallen within the acceptable range since monitoring began in 2005.  
  
Salinity \textbf{\textcolor{red}{`r icon(park_data_24[park_data_24$CharacteristicName=="Salinity",])`}}    
**Acceptable values:** Below `r park_data_24$threshold[park_data_24$CharacteristicName=="Salinity"]` `r park_data_24$unit[park_data_24$CharacteristicName=="Salinity"]`  
**2024 range:** `r park_data_24$min[park_data_24$CharacteristicName=="Salinity"]` – `r park_data_24$max[park_data_24$CharacteristicName=="Salinity"]` `r park_data_24$unit[park_data_24$CharacteristicName=="Salinity"]`  
Road salt is the main cause of high salinity in NCR streams.  Salinity has not surpassed the acceptable threshold at Flowing Springs Run since 2017.  
  
Total Nitrogen \textbf{\textcolor{red}{`r icon(park_data_24[park_data_24$CharacteristicName=="Total nitrogen",])`}}   
**Acceptable values:** Below `r park_data_24$threshold[park_data_24$CharacteristicName=="Total nitrogen"]` `r park_data_24$unit[park_data_24$CharacteristicName=="Total nitrogen"]`  
**2024 range:** `r park_data_24$min[park_data_24$CharacteristicName=="Total nitrogen"]` – `r park_data_24$max[park_data_24$CharacteristicName=="Total nitrogen"]` `r park_data_24$unit[park_data_24$CharacteristicName=="Total nitrogen"]`  
Nitrogen is commonly used in agricultural fertilizers. Under high concentrations, it can adversely affect aquatic life. All total nitrogen measurements since 2016 have exceeded the acceptable threshold.  
  
Total Phosphorus \textbf{\textcolor{red}{`r icon(park_data_24[park_data_24$CharacteristicName=="Total phosphorus",])`}}   
**Acceptable values:** Below `r park_data_24$threshold[park_data_24$CharacteristicName=="Total phosphorus"]` `r park_data_24$unit[park_data_24$CharacteristicName=="Total phosphorus"]`  
**2024 range:** `r park_data_24$min[park_data_24$CharacteristicName=="Total phosphorus"]` – `r park_data_24$max[park_data_24$CharacteristicName=="Total phosphorus"]` `r park_data_24$unit[park_data_24$CharacteristicName=="Total phosphorus"]`  
Phosphorus is often a limiting nutrient in freshwater streams, meaning a small increase in phosphorus concentration can lead to algal blooms. All observations in 2024 exceeded the threshold.  
  
Water Temperature \textbf{\textcolor{red}{`r icon(park_data_24[park_data_24$CharacteristicName=="Water temperature",])`}}    
**Acceptable values:** Below `r park_data_24$threshold[park_data_24$CharacteristicName=="Water temperature"]` `r park_data_24$unit[park_data_24$CharacteristicName=="Water temperature"]`  
**2024 range:** `r park_data_24$min[park_data_24$CharacteristicName=="Water temperature"]` – `r park_data_24$max[park_data_24$CharacteristicName=="Water temperature"]` `r park_data_24$unit[park_data_24$CharacteristicName=="Water temperature"]`   
Water temperature measurements have remained below the acceptable threshold since monitoring began in 2005.  
  
**Water Quality Monitoring in the NCR**  
Data on additional water quality parameters, including depth, discharge, conductivity, and total dissolved solids, are available in the [NCRN water quality data visualizer](https://irma.nps.gov/DataStore/Reference/Profile/2237386). Visit the [NCRN water quality monitoring webpage](https://www.nps.gov/im/ncrn/water.htm) to learn more.
